---
title: "Indo-Swiss Research Database - Analysis log"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---


```{r setup, echo=F, eval =T}
rm(list = ls())
source('core_utilities.R')
using('httr','stringr','dplyr','tidyr','tidyRSS','jsonlite','lubridate','ggplot2','readxl','readr','purrr','knitr','tibble')
using('countries')

paper.details = readRDS(file = '~/Data/ISRD/publication_details.RData')
author.details = readRDS(file = '~/Data/ISRD/author_details.RData')

tot.papers = nrow(paper.details)

#report the data that we have
printo('We have ',tot.papers,' publications pulled from Web of Science and Scopus in our analysis.')

printo('The data sources of these publications are as follows - \n',round(sum(paper.details$datasource == 'Both')/tot.papers*100),"% available in both databases,\n",round(sum(paper.details$datasource == 'Scopus')/tot.papers*100),"% available only from Scopus,\n",round(sum(paper.details$datasource == 'WoS')/tot.papers*100),"% available only from Web of Science.\n")
```


#Which research areas are represented in this collaboration

The first step is identifying what research area a particular paper belongs to. For this, Web of Science provides a much cleaner classification of papers into categories and research areas. This is done based on the journal that a paper has been published in.

However, certain high impact multidisciplinary journals (listed below) 

```{r finding research areas, echo=F, eval = T}

paper.details$`source title` = str_to_title(paper.details$`source title`)

printo("This is the list of journals that are counted as 'Multidisciplinary Sciences' according to the Web of Science classification")
multi = paper.details %>% filter(`wos categories` == 'Multidisciplinary Sciences') %>% select(`source title`) %>% pull() %>% str_to_title() %>% unique()  %>% sort()
cat(str_c(multi,collapse = '\n'))

printo('This corresponds to a total of ', round(sum(paper.details$`wos categories` == 'Multidisciplinary Sciences', na.rm= T)/tot.papers*100),"% of the papers in our database")

```

