---
title: "Indo-Swiss Research Database - Analysis for Phase 1 project submission"
author: "Siddharth Bharath, Pranshu Jaiswal, Lena Robra, Manfred Max Bergman
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---


```{r setup, echo=F, eval =T, warning = F}
rm(list = ls())
source('core_utilities.R')
using('httr','stringr','dplyr','tidyr','tidyRSS','jsonlite','lubridate','ggplot2','readxl','readr','purrr','knitr','tibble', 'arrow','jsonlite')

publications_dt <- read_parquet("Data/publications_full_dataset_2000-2024.parquet")

#Retain articles - remove letters, notes, errata
#Document types are mostly derived from Scopus. Look at https://www.ilovephd.com/list-of-document-types-covered-in-scopus/ - for details of what they refer to
publications_dt = publications_dt %>% filter((grepl('(article|review|book)',`document type`) | `document type` %in% c('conference paper','dataset','proceedings paper', 'review', 'letter','editorial','paratext','report')))

#Get the Institution classification
# auth_summ = read_parquet('Data/authors_summary_in_ch.parquet')

using('googlesheets4')
inst_class = read_sheet(ss = '173RqXA8x3LISQg5NWEicH73r10D9y92XSMdx1raRyYc', sheet = 'List from OpenAlex')

#Get the paper classification
topics_class = read_sheet(ss = '1WRlXkr4LzLiv6pka8cnPz0tlmid8dbsR9VUo_u-Lh-w', sheet = 'OpenAlex_subfields')
topics_class = topics_class %>% filter(!is.na(Max_classification))

publications_dt = publications_dt %>%
mutate(primary_subfield_id = str_remove(primary_subfield_id,'subfields/')) %>%
left_join(topics_class %>% select(Research_Area = Max_classification, primary_subfield_id = subfield_id), by = 'primary_subfield_id')



```


1 overall shared publications between researchers from India and Switzerland from 2000 to 2024 (i.e. number of publications over time)



#Temporal trends in overall data

## How has the number of publications changed over time?

```{r, echo = F, fig.height=3, fig.width = 4.5, warning = F}

dat.plot.all = publications_dt %>% group_by(publication_year) %>%
summarise(total.pubs = n())
dat.plot.all = publications_dt %>% group_by(publication_year, primary_domain_name) %>%
summarise(total = n()) %>% 
filter(!is.na(primary_domain_name)) %>%
pivot_wider(names_from = primary_domain_name, values_from = total) %>% left_join(dat.plot.all)

ggplot(dat.plot.all, aes(x=publication_year, y = total.pubs)) +
theme_bw() + geom_col() + labs(x = 'Year',y = 'Number of Publications Publications', title = 'Growth in Indo-Swiss collaborative publications', subtitle = 'Annual Publication volume from 2000-2024')

ggsave('plots/total_pubs_2000_2024.jpg',height = 5.5, width = 8, units = 'in')

```


## How does this compare to global publications

```{r, echo = F, fig.height=3, fig.width = 4.5}

global.dat = read.csv('Data/Scopus 1900-2020.csv')
global.dat = global.dat %>% select(year = Publication.year, Num_global_articles = All.articles..left.axis.)

dat.plot.all = left_join(dat.plot.all,global.dat,by='year')

ggplot(dat.plot.all, aes(x = year, y = total.pubs)) +
  theme_bw() + geom_point() + geom_line(color = 'red') + scale_y_log10() +
  geom_line(mapping = aes(x = year, y = Num_global_articles), color = 'black') +
  labs(title = 'Growth in Indo-Swiss collaborative publications between 2000 and 2024',subtitle = 'Across all research fields', x = 'Year', y = 'Number of Publications')


```

The total number of publications that are coauthored by Indian and Swiss researchers has increased from `r dat.plot.all$total.pubs[1]` in year 2000 to `r dat.plot.all$total.pubs[25]` in year 2025, which is a ``r round(dat.plot.all$total.pubs[25]/dat.plot.all$total.pubs[1],0)`-fold increase over 24 years. In the 20 years from 2000 - 2020, the number of publications indexed within Scopus increased from 0.9 million publications, to 2.5 million. This is only a 2.8 fold increase ^[Data of total number of entries in Scopus by year is gotten from Mike Thelwall, Pardeep Sud; Scopus 1900–2020: Growth in articles, abstracts, countries, fields, and journals. Quantitative Science Studies 2022; 3 (1): 37–50. doi: https://doi.org/10.1162/qss_a_00177]. OpenAlex records 3.5 million publications in the year 2000 as against 9.2 million publications in 2024, a 2.6 fold increase over that duration. 

# Which research areas are represented in this collaboration


Let's make some visualisations of how publications in different categories have changed over time.

## How are different domains growing?

```{r, echo = F, fig.height=3, fig.width = 4.5}

dat.plot = dat.plot.all %>% pivot_longer(`Health Sciences`:`Social Sciences`, names_to = 'Domain', values_to = 'publications')

ggplot(dat.plot, aes(x=publication_year, y = publications, color = Domain)) +
theme_bw() + geom_line() + labs(x = 'Year',y = 'Annual Publications', title = 'Growth in different domains')

```
2 publications associated with health, SSH, big data, and space science from 2000 to 2024 (i.e. it was aeronautics and something else according to the Leiden categorization)(i.e. four large topics over time)

```{r Max topical area classification, echo = F, eval = T}

dat.plot = publications_dt %>% filter(!is.na(Research_Area)) %>% group_by(publication_year,`Research_Area`) %>%
summarise(publications = n(),.groups = 'drop')

p1 = ggplot(dat.plot, aes(x=publication_year, y = publications, color = Research_Area, shape = Research_Area)) +
theme_bw() + geom_line() + geom_point() + labs(x = 'Year',y = 'Annual Publications', title = 'Growth of different research areas', subtitle = 'Annual publication volume from 2000-2024')

ggsave('plots/Max_research_areas_2000-2024.jpg',p1,width = 8, height =5.5, units = 'in', scale = 0.8)

```
3-6 one graph for each of the subtopics of health, SSH, big data, and space science between 2000 and 2024 (the middle range detail according to the Leiden classification, not the very fine/detailed one)


```{r Drilling into each research area, echo = F, fig.height=4.5, fig.width = 6}

dat.plot = publications_dt %>% 
filter(!is.na(Research_Area)) %>% group_by(primary_field_name, primary_subfield_name, publication_year) %>%
summarise(total.pubs = n(), .groups = 'drop')

library(RColorBrewer)
library(scales)
library(patchwork)
library(data.table)

publications_dt = as.data.table(publications_dt)
# setnames(publications_dt, 'Max_classification','Research_Area')

# Create analysis period groupings
# Group years into 5-year periods for clearer trend visualization
publications_dt[, period := cut(publication_year, 
                               breaks = c(1999, 2004, 2009, 2014, 2019, 2024),
                               labels = c("2000-04", "2005-09", "2010-14", 
                                        "2015-19", "2020-24"),
                               include.lowest = TRUE)]


for (i in unique(publications_dt$Research_Area)) {
  if(is.na(i)) next
  dat.plot = publications_dt[Research_Area == i]
  if( i %in% c('Big Data', 'Space')) {sub_area = 'primary_subfield_name'}
  if(i %in% c('Health', 'SSH')) {sub_area = 'primary_field_name'}
  setnames(dat.plot,sub_area,'Research_subfield')
  dat = dat.plot %>% as_tibble() %>% group_by(period,Research_subfield) %>%
summarise(publications = n())
  p1 = ggplot(data = dat, aes(x = period,y = publications)) +
theme_bw() + geom_col() + facet_wrap(~Research_subfield, scales = 'free') + labs(x = 'Period', y = 'Publications', title = paste0('Growth of Publications in ',i, ' split into research areas'))
ggsave(plot = p1,filename = paste0('plots/',i,'_growth_bars.jpg'), height = 7, width = 10, units = 'in', scale = ifelse(i == 'Space',0.7,0.9))
}



```


# How are various Swiss Universities contributing to the Indo-Swiss collaboration?


11 one graph for each of the topics of health, SSH, big data, and space science by Swiss universities of applied sciences between 2000 and 2024 (only those who have some collaborations with India – probably not many)

```{r institution setup, echo = F, eval = T}

#Read main publication dataset with institutional summary
# publications_institutional_summary = read_parquet("Data/publications_with_institutional_summary.parquet")

# Read the detailed publication-institution mapping
publications_with_institutions = read_parquet("Data/publications_institutional_detailed.parquet")

View(head(publications_with_institutions %>% select(title, primary_subfield_name, primary_subfield_id, contains('institution'))))

publications_with_institutions = publications_with_institutions %>% 
mutate(primary_subfield_id = str_remove(primary_subfield_id,'subfields/')) %>%
left_join(topics_class %>% select(Research_Area = Max_classification, primary_subfield_id = subfield_id), by = 'primary_subfield_id')

# head(publications_with_institutions$primary_subfield_id)
# head(topics_class$subfield_id)

# table(publications_with_institutions$Research_Area)

# Read institution trend data
# institution_trends = read_parquet("Data/institution_trends_by_year_field.parquet")

# Read top institutions by field
# top_institutions_by_field = read_parquet("Data/top_institutions_by_field.parquet")

table(publications_with_institutions$institutional_group)

institution_trends <- publications_with_institutions %>%
  filter(has_institutional_data & !is.na(Research_Area)) %>%
  # filter(institutional_group %in% c('Cantonal Universities', 'ETH','Universities of Applied Sciences')) %>% 
  mutate(period = cut(publication_year, 
                      breaks = c(1999, 2004, 2009, 2014, 2019, 2024),
                      labels = c("2000-04", "2005-09", "2010-14", 
                               "2015-19", "2020-24"),
                      include.lowest = TRUE))  %>%
  group_by(
    institution_name, 
    period,
    Research_Area,
    institutional_group
  ) %>%
  summarise(
    n_publications = length(unique(work_id)),
    # total_citations = sum(cited_by_count, na.rm = TRUE),
    # mean_citations = mean(cited_by_count, na.rm = TRUE),
    # median_citations = median(cited_by_count, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(institution_name = str_to_title(institution_name) %>% 
  str_replace('Ecole Polytechnique Federale De Lausanne', 'EPFL') %>% str_replace('Eth Zurich', 'ETH Zurich')) 


```

7-10 one graph for each of the topics of health, SSH, big data, and space science by Swiss universities between 2000 and 2024 (one line per university: 2 Federal Institutes of Technology, 10 Cantonal Universities)

```{r Different Swiss universities on each of the topics, echo = F, eval = T, warning = F }


dat.plot = institution_trends %>% 
  filter(institutional_group %in% c('Cantonal Universities', 'ETH')) %>%
  # Create summarized data
  group_by(Research_Area, period, institution_name) %>%
  summarise(total_pubs = sum(n_publications), .groups = "drop") %>%
  # Create complete grid with all combinations
  ungroup() %>% complete(Research_Area, period, institution_name) %>%
  mutate(total_pubs = replace_na(total_pubs,0))
  


for (i in unique(dat.plot$Research_Area)) {
  if(is.na(i)) next
  dat = dat.plot %>% as_tibble() %>% 
  filter(Research_Area == i) 

  p1 = ggplot(data = dat, aes(x = period,y = total_pubs)) +
theme_bw() + geom_col() + facet_wrap(~institution_name) + labs(x = 'Period', y = 'Publications', title = paste0('Research Area: ',i, ''))
ggsave(plot = p1,filename = paste0('plots/cantonal_y_',i,'.jpg'), 
height = 7, width = 10, units = 'in', scale = ifelse(i == 'Space',1.1,1.1))
}


dat.plot = institution_trends %>% 
  filter(institutional_group %in% c('Universities of Applied Sciences')) %>%
  # Create summarized data
  group_by(Research_Area, period, institution_name) %>%
  summarise(total_pubs = sum(n_publications), .groups = "drop") %>%
  # Create complete grid with all combinations
  ungroup() %>% complete(Research_Area, period, institution_name) %>%
  mutate(total_pubs = replace_na(total_pubs,0)) %>%
  mutate(institution_name = str_to_title(institution_name)) %>%
  mutate(institution_name = case_match( institution_name,
  "Bern University Of Applied Sciences" ~ "BFH",
  "Fhnw University Of Applied Sciences And Arts" ~ "FHNW", 
  "Hes-So Geneve" ~ "HES-SO Geneva",
  "Hes-So University Of Applied Sciences And Arts Western Switzerland" ~ "HES-SO",
  "Hes-So Valais-Wallis" ~ "HES-SO Valais",
  "Lucerne University Of Applied Sciences And Arts" ~ "HSLU",
  "Ostschweizer Fachhochschule Ost" ~ "OST",
  "Padagogische Hochschule Bern" ~ "PHBern",
  "School Of Engineering And Architecture Of Fribourg" ~ "HEIA-FR",
  "University Of Applied Sciences And Arts Of Southern Switzerland" ~ "SUPSI",
  "Zhaw Zurich University Of Applied Sciences" ~ "ZHAW",
  .default = NA  # ignore no match
)
  )
  


for (i in unique(dat.plot$Research_Area)) {
  if(is.na(i)) next
  dat = dat.plot %>% as_tibble() %>% 
  filter(Research_Area == i & !is.na(institution_name)) 

  inst_keep = dat %>% group_by(institution_name) %>% summarise(total = sum(total_pubs), .groups = 'drop') %>%
    filter(total > 0) %>% pull(institution_name)

  p1 = ggplot(data = dat %>% filter(institution_name %in% inst_keep), aes(x = period,y = total_pubs)) +
theme_bw() + geom_col() + facet_wrap(~institution_name) + labs(x = 'Period', y = 'Publications', title = paste0('Research Area: ',i, ''))
ggsave(plot = p1,filename = paste0('plots/uas_y_',i,'.jpg'), 
height = 7, width = 10, units = 'in', scale = ifelse(i == 'Space',1.1,1.1))
}





ggplot(dat.plot,aes(x = period,y = total_pubs)) + geom_line() + geom_point() + theme_bw() + labs(title = 'Growth in Indo-Swiss collaborative publications', subtitle = 'Split by Swiss institutional categories', x = 'Year', y = 'Number of Annual Publications') + theme(legend.title=element_blank())

ggsave('plots/institutional_group_split_2000_2024.png', width = 7, height = 4, scale = 1.2)



```


