---
title: "Indo-Swiss Research Database - Analysis for Phase 1 project submission"
author: "Siddharth Bharath, Pranshu Jaiswal, Lena Robra, Manfred Max Bergman
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---


```{r setup, echo=F, eval =T}
rm(list = ls())
source('core_utilities.R')
using('httr','stringr','dplyr','tidyr','tidyRSS','jsonlite','lubridate','ggplot2','readxl','readr','purrr','knitr','tibble', 'arrow','jsonlite')

papers <- read_parquet("Data/publications_compiled_2000-2024.parquet")

#Retain articles - remove letters, notes, errata
#Document types are mostly derived from Scopus. Look at https://www.ilovephd.com/list-of-document-types-covered-in-scopus/ - for details of what they refer to
papers = papers %>% filter((grepl('(article|review|book)',`document type`) | `document type` %in% c('conference paper','dataset','proceedings paper', 'review', 'letter','editorial','paratext','report')))



```


#Temporal trends in overall data

## How has the number of publications changed over time?

```{r, echo = F, fig.height=3, fig.width = 4.5, warning = F}

dat.plot.all = papers %>% group_by(publication_year) %>%
summarise(total.pubs = n())
dat.plot.all = papers %>% group_by(publication_year, primary_domain_name) %>%
summarise(total = n()) %>% 
filter(!is.na(primary_domain_name)) %>%
pivot_wider(names_from = primary_domain_name, values_from = total) %>% left_join(dat.plot.all)

ggplot(dat.plot.all, aes(x=publication_year, y = total.pubs)) +
theme_bw() + geom_line() + labs(x = 'Year',y = 'Annual Publications', title = 'Total collaborative publications')

```


## How does this compare to global publications

```{r, echo = F, fig.height=3, fig.width = 4.5}

global.dat = read.csv('Data/Scopus 1900-2020.csv')
global.dat = global.dat %>% select(year = Publication.year, Num_global_articles = All.articles..left.axis.)

dat.plot.all = left_join(dat.plot.all,global.dat,by='year')

ggplot(dat.plot.all, aes(x = year, y = total.pubs)) +
  theme_bw() + geom_point() + geom_line(color = 'red') + scale_y_log10() +
  geom_line(mapping = aes(x = year, y = Num_global_articles), color = 'black') +
  labs(title = 'Growth in Indo-Swiss collaborative publications between 2000 and 2024',subtitle = 'Across all research fields', x = 'Year', y = 'Number of Publications')


```

The total number of publications that are coauthored by Indian and Swiss researchers has increased from `r dat.plot.all$total.pubs[1]` in year 2000 to `r dat.plot.all$total.pubs[25]` in year 2025, which is a ``r round(dat.plot.all$total.pubs[25]/dat.plot.all$total.pubs[1],0)`-fold increase over 24 years. In the 20 years from 2000 - 2020, the number of publications indexed within Scopus increased from 0.9 million publications, to 2.5 million. This is only a 2.8 fold increase ^[Data of total number of entries in Scopus by year is gotten from Mike Thelwall, Pardeep Sud; Scopus 1900–2020: Growth in articles, abstracts, countries, fields, and journals. Quantitative Science Studies 2022; 3 (1): 37–50. doi: https://doi.org/10.1162/qss_a_00177]. OpenAlex records 3.5 million publications in the year 2000 as against 9.2 million publications in 2024, a 2.6 fold increase over that duration. 

# Which research areas are represented in this collaboration


Let's make some visualisations of how publications in different categories have changed over time.

## How are different domains growing?

```{r, echo = F, fig.height=3, fig.width = 4.5}

dat.plot = dat.plot.all %>% pivot_longer(`Health Sciences`:`Social Sciences`, names_to = 'Domain', values_to = 'publications')

ggplot(dat.plot, aes(x=publication_year, y = publications, color = Domain)) +
theme_bw() + geom_line() + labs(x = 'Year',y = 'Annual Publications', title = 'Growth in different domains')

```

```{r, echo = F, fig.height=4.5, fig.width = 6}

dat.plot = papers %>% 
filter(!is.na(primary_domain_name)) %>% group_by(primary_domain_name, primary_field_name, publication_year) %>%
summarise(total.pubs = n(), .groups = 'drop')

library(RColorBrewer)
library(scales)
library(patchwork)

# Assuming your data is in dat.plot
# Create the main visualization with faceting

# First, let's create a comprehensive faceted plot
create_publication_trends_plot <- function(dat.plot) {
  
  # Calculate some summary statistics for better plotting
  field_totals <- dat.plot %>%
    group_by(primary_domain_name, primary_field_name) %>%
    summarise(total_publications = sum(total.pubs),
              avg_annual = mean(total.pubs),
              .groups = "drop") %>%
    arrange(primary_domain_name, desc(total_publications))
  
  # Create a custom color palette for domains
  domain_colors <- c(
    "Health Sciences" = "#E31A1C",
    "Life Sciences" = "#33A02C", 
    "Physical Sciences" = "#1F78B4",
    "Social Sciences" = "#FF7F00"
  )
  
  # Main plot with facets by domain
  p1 <- dat.plot %>%
    ggplot(aes(x = publication_year, y = total.pubs, color = primary_domain_name)) +
    geom_line(aes(group = primary_field_name), alpha = 0.7, linewidth = 0.8) +
    geom_point(size = 1.5, alpha = 0.8) +
    geom_smooth(aes(group = primary_field_name), method = "loess", se = FALSE, 
                size = 0.5, alpha = 0.6) +
    facet_wrap(~primary_domain_name, scales = "free_y", ncol = 2) +
    scale_color_manual(values = domain_colors) +
    scale_x_continuous(breaks = seq(2005, 2025, 5)) +
    scale_y_continuous(labels = comma_format()) +
    labs(
      title = "Publication Trends by Research Field Over Time",
      subtitle = "Trends shown by domain with individual field trajectories",
      x = "Publication Year",
      y = "Number of Publications",
      color = "Domain",
      caption = "Data: Enhanced Research Publication Dataset (OpenAlex + WoS + Scopus)"
    ) +
    theme_minimal() +
    theme(
      plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
      plot.subtitle = element_text(size = 12, hjust = 0.5, color = "gray60"),
      strip.text = element_text(size = 11, face = "bold"),
      legend.position = "none", # Remove legend since domain is in facet titles
      panel.grid.minor = element_blank(),
      panel.grid.major.x = element_line(color = "gray90", size = 0.5),
      panel.grid.major.y = element_line(color = "gray90", size = 0.5),
      axis.text.x = element_text(angle = 45, hjust = 1)
    )
  
  return(p1)
}

# Create detailed field-level plots for each domain
create_field_detail_plots <- function(dat.plot) {
  
  # Get top fields by total publications in each domain
  top_fields <- dat.plot %>%
    group_by(primary_domain_name, primary_field_name) %>%
    summarise(total = sum(total.pubs), .groups = "drop") %>%
    group_by(primary_domain_name) %>%
    top_n(6, total) %>%
    ungroup()
  
  # Filter data to top fields only
  dat_filtered <- dat.plot %>%
    semi_join(top_fields, by = c("primary_domain_name", "primary_field_name"))
  
  # Create separate plots for each domain
  plot_list <- list()
  domains <- unique(dat_filtered$primary_domain_name)
  
  for(domain in domains) {
    domain_data <- dat_filtered %>% filter(primary_domain_name == domain)
    
    # Get distinct colors for fields within domain
    n_fields <- length(unique(domain_data$primary_field_name))
    colors <- brewer.pal(min(n_fields, 11), "Spectral")
    
    p <- domain_data %>%
      ggplot(aes(x = publication_year, y = total.pubs, color = primary_field_name)) +
      geom_line(linewidth = 1.2, alpha = 0.8) +
      geom_point(size = 2) +
      scale_color_manual(values = colors) +
      scale_x_continuous(breaks = seq(2005, 2025, 5)) +
      scale_y_continuous(labels = comma_format()) +
      labs(
        title = paste("Top Fields in", domain),
        x = "Publication Year",
        y = "Number of Publications",
        color = "Field"
      ) +
      theme_minimal() +
      theme(
        plot.title = element_text(size = 14, face = "bold"),
        legend.position = "bottom",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9),
        axis.text.x = element_text(angle = 45, hjust = 1),
        panel.grid.minor = element_blank()
      ) +
      guides(color = guide_legend(ncol = 2))
    
    plot_list[[domain]] <- p
  }
  
  return(plot_list)
}

# Create heatmap visualization
create_heatmap_plot <- function(dat.plot) {
  
  # Create a heatmap of publication intensity
  heatmap_data <- dat.plot %>%
    group_by(primary_domain_name, primary_field_name) %>%
    summarise(total_pubs = sum(total.pubs), .groups = "drop") %>%
    group_by(primary_domain_name) %>%
    mutate(pct_of_domain = total_pubs / sum(total_pubs) * 100) %>%
    ungroup()
  
  # Keep only top fields per domain for readability
  top_fields_heatmap <- heatmap_data %>%
    group_by(primary_domain_name) %>%
    top_n(8, total_pubs) %>%
    ungroup()
  
  p_heatmap <- top_fields_heatmap %>%
    ggplot(aes(x = primary_domain_name, y = reorder(primary_field_name, total_pubs), 
               fill = total_pubs)) +
    geom_tile(color = "white", size = 0.5) +
    geom_text(aes(label = comma(total_pubs)), color = "white", size = 3, fontface = "bold") +
    scale_fill_gradient(low = "lightblue", high = "darkblue", 
                       labels = comma_format(), name = "Total\nPublications") +
    labs(
      title = "Publication Volume by Field and Domain",
      subtitle = "Top fields shown per domain",
      x = "Domain",
      y = "Field"
    ) +
    theme_minimal() +
    theme(
      plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
      plot.subtitle = element_text(size = 12, hjust = 0.5, color = "gray60"),
      axis.text.x = element_text(angle = 45, hjust = 1),
      axis.text.y = element_text(size = 9),
      panel.grid = element_blank()
    )
  
  return(p_heatmap)
}

# Execute the visualizations
main_plot <- create_publication_trends_plot(dat.plot)
field_plots <- create_field_detail_plots(dat.plot)
heatmap_plot <- create_heatmap_plot(dat.plot)

# Display main plot
print(main_plot)

# Display field detail plots
for(i in 1:length(field_plots)) {
  print(field_plots[[i]])
}

# Display heatmap
print(heatmap_plot)

# Create a summary table
summary_table <- dat.plot %>%
  group_by(primary_domain_name, primary_field_name) %>%
  summarise(
    total_publications = sum(total.pubs),
    years_active = n(),
    avg_annual = round(mean(total.pubs), 1),
    peak_year = publication_year[which.max(total.pubs)],
    peak_publications = max(total.pubs),
    .groups = "drop"
  ) %>%
  arrange(primary_domain_name, desc(total_publications))

print("Summary Statistics by Field:")
print(summary_table)

# Calculate growth rates for fields with sufficient data
growth_analysis <- dat.plot %>%
  group_by(primary_domain_name, primary_field_name) %>%
  arrange(publication_year) %>%
  summarise(
    first_year = min(publication_year),
    last_year = max(publication_year),
    first_year_pubs = total.pubs[which.min(publication_year)],
    last_year_pubs = total.pubs[which.max(publication_year)],
    total_pubs = sum(total.pubs),
    .groups = "drop"
  ) %>%
  filter(last_year - first_year >= 5) %>%  # At least 5 years of data
  mutate(
    growth_rate = ((last_year_pubs - first_year_pubs) / first_year_pubs) * 100,
    annual_growth = growth_rate / (last_year - first_year)
  ) %>%
  arrange(desc(annual_growth))

print("Annual Growth Rates by Field (fields with 5+ years of data):")
print(growth_analysis)

```


# How has the composition of research keywords changed over 25 years

We examine all the papers in two 5 year periods - 2000-2004 and 2020-2024. In case author keywords are not provided for a paper, we have used the keywords that are generated by Web of Science or Scopus. Below are visualisations of the most common keywords using a word cloud.

## Research keywords in the period of 2000 - 2004

```{r Keywords at the start of the period, echo = F, warning = F, fig.height = 6, fig.width = 9}
using('wordcloud', 'RColorBrewer')

keywords_start = paper.details %>% filter(year >= 2000 & year <= 2004) %>%
  select(year,`author keywords`,keywords_plus_wos,index_keywords_scopus) %>%
  mutate(keywords = ifelse(!is.na(`author keywords`), 
                           `author keywords`,
                           ifelse(!is.na(keywords_plus_wos), 
                                  keywords_plus_wos,
                                  index_keywords_scopus))) %>%
  filter(!is.na(keywords))

printo('There are ',nrow(keywords_start),' publications with keywords in the 5 year period between 2000 and 2004')

keylist1 = keywords_start %>% select(keywords) %>%
  separate_longer_delim(keywords,delim = ';') %>% mutate(keywords = keywords %>% str_squish() %>% str_to_lower()) %>% group_by(keywords) %>% summarise(freq = n()) %>% arrange(desc(freq))

wordcloud(words = keylist1$keywords, freq = keylist1$freq,scale = c(3,0.5),
          max.words = 100, min.freq = keylist1$freq[1]/20, random.order = FALSE, rot.per = 0.35,         colors = brewer.pal(8, "Dark2"))

rm(keywords_start,keylist1)

```

## Research in the period 2020 to 2024


```{r Keywords at the end of the period, echo = F, warning=F, fig.height = 6, fig.width = 9}

keywords_end = paper.details %>% filter(year >= 2020 & year <= 2024) %>%
  select(year,`author keywords`,keywords_plus_wos,index_keywords_scopus) %>%
  mutate(keywords = ifelse(!is.na(`author keywords`), 
                           `author keywords`,
                           ifelse(!is.na(keywords_plus_wos), 
                                  keywords_plus_wos,
                                  index_keywords_scopus))) %>% filter(!is.na(keywords))

printo('There are ',nrow(keywords_end),' publications with keywords in the 5 year period between 2020 and 2024')


keylist2 = keywords_end  %>% select(keywords) %>%
  separate_longer_delim(keywords,delim = ';') %>% mutate(keywords = keywords %>% str_squish() %>% str_to_lower() %>% str_replace('^humans','human')) %>% group_by(keywords) %>% summarise(freq = (n())) %>% arrange(desc(freq)) %>%
  filter(keywords != 'article')

#human is the largest keyword by far, skewing the wordcloud, so we cut it down
keylist2$freq[1] = keylist2$freq[2]

wordcloud(words = keylist2$keywords, freq = keylist2$freq,scale = c(3,0.5),
          max.words = 100, min.freq = keylist2$freq[1]/20, random.order = FALSE, rot.per = 0.35,         colors = brewer.pal(8, "Dark2"))

rm(keywords_end,keylist2)

```

# Identifying the institutions conducting research

```{r Mapping author data to institutions, echo = F, eval = T}

author.details = readRDS(file = 'Data/author_details.RData')


dat1 = author.details %>% unnest(author_details) 


dat1 = dat1 %>% 
  filter(country %in% c('India','Switzerland'))
  # mutate(primary_institution = str_split(institution, ",", simplify = TRUE)[,1] %>% str_to_lower())

swiss_inst_cleaned = read_csv(file = 'Data/institutions_standardized_output_swiss.csv', show_col_types = F) %>% select(-nPapers,-nAuth) #%>% rename(primary_institution = institution)

dat2 = dat1 %>% filter(country == 'Switzerland') %>% left_join(swiss_inst_cleaned, by = join_by(datasource, institution, country)) %>%
  rename(institution_std = `standardized name`)
# View(dat2 %>% filter(`standardized name` == '---'))

rm(dat1,swiss_inst_cleaned)

```


```{r Graph the change in publications for the different institutional domains, echo = F, eval = T}

dat2 = dat2 %>% 
  mutate(inst_group = 
           ifelse(institution_std %in% c('University of Geneva - GE', 'University of Applied Sciences and Arts Western Switzerland - HES-SO', 'University of Berne - BE', 'University of Zurich - ZH', 'University of Basel - BS','University of Fribourg - FR', 'University of Lausanne - LA', 'University of Neuchatel - NE','University of Lucerne - LU','Università della Svizzera italiana - USI','University Hospital Basel - BS'),
                  'Cantonal', 
                  ifelse(institution_std %in% c('ETH Zurich - ETHZ','EPF Lausanne - EPFL'), 'ETH','Others')))

dat2.1 = dat2 %>% 
  left_join(paper.details %>% select(pubNum,year), by = 'pubNum') %>%
  group_by(year,inst_group) %>%
  summarise(num_publications = length(unique(pubNum)), .groups ='drop') %>%
  filter(year < 2025)

ggplot(data = dat2.1 %>% filter(inst_group!='Others'), mapping = aes(x = year, y = num_publications, color = inst_group)) +
  theme_bw() + geom_line() + geom_point() +
  labs(title = 'Joint Indo-Swiss publications between 2000 and 2024', x = 'Year', y = 'Number of Publications')
ggsave('byinst.png', height = 6, width = 9)

```


