---
title: "Indo-Swiss Research Database - Data import and processing log"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

This [R Markdown](http://rmarkdown.rstudio.com) Notebook is running and logging the import of data from raw CSV files and carrying out initial processing. It makes note of all analysis and cleaning decisions made while gathering the data.

```{r Setup, echo=F, warning = F}
#This script imports from raw CSV files of Web of Science and Scopus
rm(list = ls())
source('core_utilities.R')
using('httr','stringr','dplyr','tidyr','tidyRSS','jsonlite','lubridate','ggplot2','readxl','readr','purrr','knitr','tibble')
using('countries','arrow')


```

```{r Import data, echo = F, eval = T}

#ONLY RUN THIS IF YOU HAVE NEW DATA TO ADD IN.

# Importing from WoS -------------------------------

#Importing from Web of Science export
source.files = list.files(path = '~/Data/ISRD/source_data',pattern= 'wos',full.names =T, ignore.case = T)

wosdat = tibble()
for(i in source.files) {
  dati = read_xls(i,col_types='text') #%>% mutate(sourcefile = i)
  # print(i)
  # print(sum(is.na(dati$Addresses)))
  wosdat = bind_rows(wosdat,dati)
}
rm(dati,i)
wosdat = distinct(wosdat)


# Importing from Scopus ---------------------------------------------------

source.files = list.files(path = '~/Data/ISRD/source_data',pattern= 'scopus',full.names =T,ignore.case = T)

scodat = tibble()
for(i in source.files) {
  dati = read_csv(i,col_types = rep('c',46))
  scodat = bind_rows(scodat,dati)
}
rm(dati,i)
scodat = distinct(scodat)

#Harmonise the names between different datasets
names(wosdat) = tolower(names(wosdat))
names(scodat) = tolower(names(scodat))


#Get a list of column names to work with
# cat(str_c(names(wosdat),collapse ='\n'))

#Read the column matching tables
wosnames = read.csv(file = 'prep-tables/wos_names_for_merging.csv')
sconames = read.csv(file = 'prep-tables/scopus_names_for_merging.csv')

# Identify the names to drop
drop_names <- sconames %>% 
  filter(name_to == "IGNORE") %>% 
  pull(scopus_names)

# Create a renaming vector for those not to ignore
rename_vec <- sconames %>% 
  filter(name_to != "IGNORE") %>% 
  transmute(new = name_to,old = scopus_names) %>%
  deframe()

# Remove the columns and then rename
scodat <- scodat %>% 
  select(-one_of(drop_names)) %>% 
  rename(!!!rename_vec)

#Now do it for web of science
# Identify the names to drop
drop_names <- wosnames %>% 
  filter(name_to == "IGNORE") %>% 
  pull(wos_names)

# Create a renaming vector for those not to ignore
rename_vec <- wosnames %>% 
  filter(name_to != "IGNORE") %>% 
  transmute(new = name_to,old = wos_names) %>%
  deframe()

# Remove the columns and then rename
wosdat <- wosdat %>% 
  select(-one_of(drop_names)) %>% 
  rename(!!!rename_vec)

rm(wosnames,sconames,drop_names,rename_vec)

#Check that they are Indo-Swiss collaborations
# the column 'affiliations' in scopus contains the country
# the column 'authors with affiliations' in web of science contains the country
wosdat = wosdat %>% 
  mutate(swiss = grepl('switzerland',`authors with affiliations`,ignore.case=T), india = grepl('india',`authors with affiliations`,ignore.case=T)) %>%
  # mutate(swiss = grepl('switzerland',`addresses`,ignore.case=T), india = grepl('india',`addresses`,ignore.case=T)) %>%
  mutate(collab = case_when((swiss & india) == T ~ 'Both',
                            swiss == T ~ 'Swiss',
                            india == T ~ 'India',
                            .default = 'None'))
if(any(wosdat$collab != 'Both')) {
  printo('The Web of Science raw data includes papers that do not have both Indian and Swiss affiliations. Cleaning them out.')
}
# wosdat1 = wosdat %>% filter(collab != 'Both') %>% select(-swiss,-india,-collab)
wosdat = wosdat %>% filter(collab == 'Both') %>% select(-swiss,-india,-collab)

scodat = scodat %>% 
  mutate(swiss = grepl('switzerland',affiliations,ignore.case=T), india = grepl('india',affiliations,ignore.case=T)) %>%
  mutate(collab = case_when((swiss & india) == T ~ 'Both',
                            swiss == T ~ 'Swiss',
                            india == T ~ 'India',
                            .default = 'None'))
if(any(scodat$collab != 'Both')) {
  printo('The Scopus raw data includes papers that do not have both Indian and Swiss affiliations. Cleaning them out.')
}
scodat = scodat %>% filter(collab == 'Both') %>% select(-swiss,-india,-collab)

saveRDS(scodat,file = '~/Data/ISRD/raw_scopus.RData')
saveRDS(wosdat,file = '~/Data/ISRD/raw_webofscience.RData')

```

```{r,eval=T, echo=F}
scodat = readRDS(file = '~/Data/ISRD/raw_scopus.RData')
wosdat = readRDS(file = '~/Data/ISRD/raw_webofscience.RData')
```

## Summaries of the initial data files

```{r,eval=T, echo=F, eval = T}

printo("The Web of Science data consists of ",nrow(wosdat), " entries, ranging from ", min(wosdat$`year`), " to ", max(wosdat$`year`),".")
printo()
printo("The Scopus data consists of ",nrow(scodat), " entries, ranging from ", min(scodat$`year`), " to ", max(scodat$`year`),".")

```

We are now exploring how to match the datasets. One easy way to match is to use doi (digital object identifiers), which are created for this express purpose

```{r doi for WoS Data, echo = F, eval = T}


printo('For the WoS data, ',sum(!is.na(wosdat$doi)), " out of ", nrow(wosdat), ' entries have a doi. That corresponds to ', round(sum(!is.na(wosdat$doi))/nrow(wosdat)*100),'%.')

wosdat = wosdat %>% mutate(times_cited = as.numeric(times_cited), doi = tolower(doi))
wos.doi = wosdat %>% filter(!is.na(doi))%>% group_by(doi) %>% summarise(count = n()) %>% arrange(desc(count)) %>% filter(count > 1)
printo('Within this dataset, there are ',nrow(wos.doi),' dois that are not unique. Looking in and cleaning them.')
wos.doi.forclean = wosdat %>% filter(!is.na(doi)) %>% filter(doi %in% wos.doi$doi) %>% arrange(doi)
wos.doi = wosdat %>% filter(!is.na(doi)) %>% filter(!(doi %in% wos.doi$doi))

printo()
printo('Mostly these are situations where there are small variations and duplications. We clean these duplicates with the following rules - First prioritise those which have more citations, then which have more complete ORCID IDs.')

wos.doi.cleaning = wos.doi.forclean %>% 
  arrange(doi,desc(times_cited),desc(orcids)) %>% group_by(doi) %>% slice_head(n = 1)

wos.doi = bind_rows(wos.doi, wos.doi.cleaning)
rm(wos.doi.forclean,wos.doi.cleaning)
printo()
printo('These are cleaned now, and we have ',nrow(wos.doi),' publications with a unique doi from Web of Science.')


printo()

```

```{r doi for Scopus data, echo = F, eval = T}

printo('For the Scopus data, ',sum(!is.na(scodat$doi)), " out of ", nrow(scodat), ' entries have a doi. That corresponds to ', round(sum(!is.na(scodat$doi))/nrow(scodat)*100),'%.')
scodat = scodat %>% mutate(doi = tolower(doi))

sco.doi = scodat %>% 
  filter(!is.na(doi))%>% group_by(doi) %>% summarise(count = n()) %>% arrange(desc(count)) %>% filter(count > 1)
printo('Within this dataset, there are ',nrow(sco.doi),' dois that are not unique. Looking into them deeper.')
sco.doi.forclean = scodat %>% filter(!is.na(doi)) %>% filter(doi %in% sco.doi$doi) %>% arrange(doi)
sco.doi = scodat %>% filter(!is.na(doi)) %>% filter(!(doi %in% sco.doi$doi))

printo()
printo('Mostly these are situations where the same authors have written the preface to a book and a chapter within the book, or where a publication is duplicated in some way. We clean these duplicates with the following rules - First prioritise those which have abstracts, then prioritise those which have more citations, then prioritise those that were published earlier.')

sco.doi.forclean$abstract = na_if(sco.doi.forclean$abstract,"[No abstract available]")

sco.doi.cleaning = sco.doi.forclean %>% mutate(isAbstract = is.na(abstract)) %>% arrange(doi,isAbstract,desc(times_cited),year) %>% group_by(doi) %>% slice_head(n = 1)

sco.doi = bind_rows(sco.doi, sco.doi.cleaning)
rm(sco.doi.forclean,sco.doi.cleaning)
printo()
printo('These are cleaned now, and we have ',nrow(sco.doi),' publications with a unique doi from Scopus.')

```

Now let us try to match the two databases based on doi

```{r Matching those with doi, echo = F, eval = T}

  
allentries = full_join(sco.doi %>% mutate(scopus = 2),wos.doi %>% mutate(wos = 1), by = 'doi',suffix = c('.s','.w')) %>%
  mutate(scopus = replace_na(scopus,0), wos = replace_na(wos,0),
         year.s = as.numeric(year.s), year.w=as.numeric(year.w)) %>%
  mutate(datasource = as.character(scopus+wos)) %>%
  mutate(datasource = case_match(datasource,
                                 '3' ~ 'Both',
                                 '2' ~ 'Scopus',
                                 '1' ~ 'WoS',
                                 '0' ~ 'None')) %>%
  select(-wos,-scopus)
allentries = allentries %>% select(order(colnames(allentries)))

printo("When we match entries between the two databases using DOI, we find \n", sum(allentries$datasource == 'Both'), ' entries common to both databases\n',
       sum(allentries$datasource == 'Scopus'), ' entries only in Scopus\n',
       sum(allentries$datasource == 'WoS'), ' entries only in Web of Science.\n')

# table(allentries$datasource)

#Checking the status of matched vs unmatched entries
# matched = allentries %>% filter(datasource == 'Both')
# singles = allentries %>% filter(datasource != 'Both') %>% 
#   mutate(`article title` = ifelse(is.na(`article title.w`),`article title.s`,`article title.w`), `document type` = ifelse(is.na(`document type.w`),`document type.s`,`document type.w`)) %>% 
#   arrange(`article title`)
# single.articles = singles %>% filter(grepl('article', `document type`,ignore.case = T))


#Harmonise year and a few other columns between the two datasets
allentries = allentries %>% mutate(year = pmin(year.s,year.w,na.rm=T), yeardiff = year.s-year.w,.keep = 'unused')
# View(allentries %>% filter(abs(yeardiff)>1) %>% arrange(yeardiff))
printo('There are ', sum(abs(allentries$yeardiff)>1, na.rm = T), ' matched papers where there is a difference of publication date of more than one year between the two datasets. We are glossing over this for now and just choosing the earlier year between the two for the publications.')

# namescheck = allentries %>% filter(datasource == 'Both') %>% slice_sample(n = 200)

#Remove redundancy in columns
allentries = allentries %>%
  #For article title and document type, prefer the one from scopus instead of WoS
  mutate(`article title` = ifelse(is.na(`article title.s`),`article title.w`,`article title.s`), 
         `document type` = ifelse(is.na(`document type.s`),`document type.w`,`document type.s`),
         `publisher` = ifelse(is.na(`publisher.s`),`publisher.w`,`publisher.s`), 
         `isbn` = ifelse(is.na(`isbn.s`),`isbn.w`,`isbn.s`),
         `issn` = ifelse(is.na(`issn.s`),`issn.w`,`issn.s`),
         `open access` = ifelse(is.na(`open access.s`),`open access.w`,`open access.s`),
         `issue` = ifelse(is.na(`issue.s`),`issue.w`,`issue.s`),
         `volume` = ifelse(is.na(`volume.s`),`volume.w`,`volume.s`),
         `pubmed id` = ifelse(is.na(`pubmed id.s`),`pubmed id.w`,`pubmed id.s`),
         `language` = ifelse(is.na(`language.s`),`language.w`,`language.s`),
         `source title` = ifelse(is.na(`source title.s`),`source title.w`,`source title.s`),
         .keep = 'unused') %>%
  mutate(`page count` = pmax(as.numeric(`page count.s`),as.numeric(`page count.w`),na.rm=T),.keep = 'unused') %>% select(-yeardiff)

printo("\nFor the fields - article title, document type, publisher, isbn, issn, issue, open access, volume, pubmed id, language, source title and page count - we are prefering the Scopus data to WoS, where there is a conflict.")

printo("\nNow this dataset of ", nrow(allentries)," entries all with DOIs and matched between Scopus and Web of Science, is what we will take ahead for further analysis.")
#choose a random sample of dois to figure out column meaning and matches
# doisample = sample(matching$doi,30)
# write_csv(sco.doi %>% filter(doi %in% doisample), file = 'scopus_data_example.csv')
# write_csv(wos.doi %>% filter(doi %in% doisample), file = 'WebOfScience_data_example.csv')

allentries = allentries %>% mutate(pubNum = row_number()) %>%
  rename(addresses.s = addresses, addresses.w = `authors with affiliations`) 
allentries = allentries %>% 
  select(order(colnames(allentries))) %>%
  filter(year < 2025)

saveRDS(allentries,file = '~/Data/ISRD/matched_data.rdata')

rm(wosdat,wos.doi,scodat,sco.doi)
```




#Processing Author Information

Both Scopus and Web of Science provide their own unique identifiers for authors. We need to process the author data from each database separately, and then combine them.

```{r Starting author processing, echo = F, eval = T}
allentries = readRDS(file = '~/Data/ISRD/matched_data.rdata')
# allentries = allentries %>% slice_sample(n = 500)
# printo('Proceeding with only a subset of 500 publications, in order to check that the code is working. Once it is fully done, will move to running on the full dataset of `18,000 publications.\n')


```

First, processing the author data from Web of Science. 

```{r Processing Web of Science author data, echo = F}

dat1 = allentries %>% filter(datasource %in% c('WoS','Both')) %>% select(pubNum,`author full names.w`,addresses = addresses.w) 

allinst = tibble()

printo("Extracting data of individual authors from each publication. Using the library 'countries' to assign country identities to affiliations. You will see a report from that function below.\n")

for (i in 1:nrow(dat1)) {
  # authors = dat1$`Author Full Names`[i] %>%
  #   str_split(pattern =';',simplify=T) %>% str_trim()
  inst = dat1$addresses[i] %>% str_split(pattern = '; \\[',simplify = T) %>% str_remove('^\\[')
  inst = tibble(inst = inst) %>%
    mutate(author = str_extract(inst,'^.*(?=\\])'), institution = str_extract(inst,'(?<=\\]).*') %>% str_trim()) %>%
    # mutate(singleauthor = author %>% str_split(pattern = '; '))
    separate_longer_delim(author,'; ') %>% select(-inst) %>% mutate(pubNum = dat1$pubNum[i])
  allinst = bind_rows(allinst,inst)
  rm(inst)
}

dat2 = dat1 %>%
  separate_longer_delim(`author full names.w`,'; ') %>% rename(author = `author full names.w`) %>%
  #ensure each author full name comes only once
  distinct() %>%
  left_join(allinst,by = join_by(pubNum, author), relationship = 'one-to-many') %>%
  mutate(country = str_extract(institution, ',[^,]*$') %>% str_remove('^, ') %>% str_remove('\\(data truncated to fit\\)') %>% str_remove('.*(?=USA$)') %>% country_name(to = 'simple',verbose = T, na_fill = F))

#For each author, count whether they are only Indian, Only Swiss or both
byauth = dat2 %>% 
  group_by(pubNum,author) %>% 
  summarise(Swiss = any(country == 'Switzerland'),  India = any(country == 'India'),.groups = 'drop',nAuthCountries = length(unique(country))) %>%
  mutate(auth_cat = case_when(Swiss & India ~ 'Both',
                               Swiss ~ 'Swiss',
                               India ~ 'India', .default = 'None'))

authordat.w = dat2 %>% left_join(byauth %>% select(-Swiss,-India), by = join_by(pubNum,author)) %>% select(-addresses) %>%
  nest(author_details = author:auth_cat,.by=pubNum)


rm(allinst,byauth,dat1,dat2)
saveRDS(authordat.w,file='~/Data/ISRD/authordat_wos.rdata')
rm(authordat.w)

```

Second, processing the author data from Scopus. Scopus also provides a unique numerical ID to each author. There are some challenges to uniquely extracting that (including the issue of there being multiple people named "M. Kumar" on the same paper, but with different Scopus IDs). So I will skip extracting that for now and add it in at a later stage.


```{r Now processing authors for Scopus, echo = F}
dat1 = allentries %>% filter(datasource == 'Scopus') %>% select(pubNum,`authors.s`,`author full names.s`,addresses = addresses.s) 
rm(allentries)
allinst = tibble()

printo("Extracting data of individual authors from each publication. Using the library 'countries' to assign country identities to affiliations. You will see a report from that function below.\n")

country_match = paste0(",\\s*(", paste(list_countries(), collapse="|"), "|United States|Peoples R China)")

for (i in 1:nrow(dat1)) {
  # authors = dat1$`Author Full Names`[i] %>%
  #   str_split(pattern =';',simplify=T) %>% str_trim()
  inst = dat1$addresses[i] %>% str_split(pattern = ';',simplify = T) %>% str_squish()
  inst = tibble(inst = inst) %>%
    mutate(author = str_extract(inst,'^[^,]+') %>% str_trim(), 
           institution = str_extract(inst,'(?<=,).*') %>% str_trim()) %>%
    #There is a problem. Scopus includes multiple institutions in the field for the same author, with no specific identifier separating them.
    mutate(institution = str_replace_all(institution, country_match, ", \\1<<<SPLIT>>>") %>% str_remove('<<<SPLIT>>>$'))  %>%
    # mutate(singleauthor = author %>% str_split(pattern = '; '))
    separate_longer_delim(institution,'<<<SPLIT>>>') %>% 
    mutate(institution = str_remove(institution, '^,') %>% str_trim())
  inst = inst %>% 
    select(-inst) %>% mutate(pubNum = dat1$pubNum[i])
  allinst = bind_rows(allinst,inst)
  rm(inst)
}

# authors = dat1 %>% select(pubNum,author = authors.s) %>% separate_longer_delim(author,'; ')
# scopus_ids = dat1 %>% select(pubNum,aut = `author full names.s`) %>%
#   separate_longer_delim(aut,'; ') %>% 
#   mutate(scopus_id = str_extract(aut,"(?<=\\()[0-9]+(?=\\))")) %>% select(-aut)
# scopus_ids = cbind(authors,scopus_ids %>% select(-pubNum))# %>% distinct()
# rm(authors)

dat2 = dat1 %>%
  separate_longer_delim(`authors.s`,'; ') %>% rename(author = authors.s) %>%
  # bind_cols(scopus_ids %>% select(scopus_id)) %>% 
  select(-`author full names.s`,-addresses) %>%
  #ensure each author name comes only once
  distinct() %>% 
  # left_join(scopus_ids,by=c('pubNum','author'),relationship = 'one-to-one') %>%
  left_join(allinst,by = join_by(pubNum, author), relationship = 'one-to-many') %>%
  ## PROBLEM - the hugely coauthored papers are having multiple authors who have the same initials, but different scopus IDs, so it is not getting accurately mapped.
  mutate(country = str_extract(institution, ',[^,]*$') %>% str_remove('^, ') %>%
             #str_remove('\\(data truncated to fit\\)') %>% str_remove('.*(?=USA$)') %>%
             country_name(to = 'simple',verbose = T, na_fill = F))
  
#For each author, count whether they are only Indian, Only Swiss or both
byauth = dat2 %>% 
  group_by(pubNum,author) %>% 
  summarise(Swiss = any(country == 'Switzerland'),  India = any(country == 'India'),.groups = 'drop',nAuthCountries = length(unique(country))) %>%
  mutate(auth_cat = case_when(Swiss & India ~ 'Both',
                               Swiss ~ 'Swiss',
                               India ~ 'India', .default = 'None'))

authordat.s = dat2 %>% 
  left_join(byauth %>% select(-Swiss,-India), by = join_by(pubNum,author)) %>% #select(-addresses) %>%
  nest(author_details = author:auth_cat,.by=pubNum)

saveRDS(authordat.s,file='~/Data/ISRD/authordat_scopus.rdata')

rm(allinst,byauth,dat1,dat2)

```

Now we need to proceed to combine the author data between the two datasets. We are choosing to prioritise data from Web of Science over data from Scopus. This is because Scopus author data includes multiple institutional affiliations for the author in the same cell with no clear separator. Thus the Web of Science data is easier to clean. In case information on a particular publication is not available in Web of Science, we will get it from Scopus.

```{r Combining and cleaning author data, echo = F, eval = T}

authordat.w = readRDS(file = '~/Data/ISRD/authordat_wos.rdata')

authordat.s = readRDS(file='~/Data/ISRD/authordat_scopus.rdata')

allentries = readRDS(file = '~/Data/ISRD/matched_data.rdata')

#Give priority to WoS author data over Scopus author data, because Scopus is messier
dat1 = allentries %>% 
  filter(datasource == 'Scopus') %>%
  left_join(authordat.s,by = 'pubNum')
dat2 = allentries %>% 
  filter(datasource != 'Scopus') %>%
  left_join(authordat.w,by = 'pubNum')
dat = bind_rows(dat1,dat2)

#Check that all rows have author details
dat_filtered <- dat %>% 
  filter(map_lgl(author_details, is.null))
if(nrow(dat_filtered) != 0) {
  printo('Warning: some entries have not gotten author details')
  stop()
}
rm(dat_filtered, dat1,dat2)

#Some Early cleaning
# dat  = dat %>% filter(str_detect(`Document Type`,'^(Article|Review)'))

#add in some additional details - 
dat = dat |> mutate(nCountries = map_int(author_details, \(authors) length(unique(authors$country))),
                      nAuthors = map_int(author_details, \(authors) length(unique(authors$author))),
                      nInst = map_int(author_details, \(authors) length(unique(authors$institution))),
                      nSwissInst = map_int(author_details, \(authors) authors %>% filter(country == 'Switzerland') %>% pull(institution) %>% unique() %>% length()),
                      nIndInst = map_int(author_details, \(authors) authors %>% filter(country == 'India') %>% pull(institution) %>% unique() %>% length()),
                      nSwissAuth = map_int(author_details, \(authors) authors %>% filter(country == 'Switzerland') %>% pull(author) %>% unique() %>% length()),
                      nIndAuth = map_int(author_details, \(authors) authors %>% filter(country == 'India') %>% pull(author) %>% unique() %>% length()),
                      nBothAuth = map_int(author_details, \(authors) authors %>% filter(auth_cat == 'Both') %>% pull(author) %>% unique() %>% length()))
#For each author, count whether they are only Indian, Only Swiss or both

if(any(dat$nCountries<1) | any(is.na(dat$nCountries))) {
  printo('Warning some entries are not having data parsed down to country level.')
}

#Reduce duplication in columns
dat1 = dat %>%
  filter(datasource != 'Scopus') %>%
  rename(`author keywords` = `author keywords.w`, `correspondence address` = `correspondence address.w`, affiliations = affiliations.w, `author full names` = `author full names.w`,authors = authors.w) %>%
  select(-`author keywords.s`, -`correspondence address.s`, - affiliations.s, - `author full names.s`, - authors.s)

dat2 = dat %>%
  filter(datasource == 'Scopus') %>%
  rename(`author keywords` = `author keywords.s`, `correspondence address` = `correspondence address.s`, affiliations = affiliations.s, `author full names` = `author full names.s`,authors = authors.s) %>%
  select(-`author keywords.w`, -`correspondence address.w`, - affiliations.w, - `author full names.w`, - authors.w)

dat = bind_rows(dat1,dat2)
rm(dat1,dat2)
dat = dat %>% select(order(names(dat))) %>% select(-isAbstract)

saveRDS(dat,file = '~/Data/ISRD/matched_with_authors.RData')

rm(allentries, authordat.s,authordat.w)

paper.details = dat %>%
  select(-author_details, - `email addresses`, -reasearcherID_wos,-author_scopus_id,-addresses.s,-addresses.w,-`open access`,-orcids)

author.details = dat %>%
  select(pubNum,datasource,author_details,`source title`,nAuthors:nSwissInst,`email addresses`,addresses.s,addresses.w)

saveRDS(paper.details,file = 'Data/publication_details.RData')
saveRDS(author.details,file = 'Data/author_details.RData')

write_feather(paper.details, 'Data/publication_details.feather', compression = 'zstd', compression_level = 5)
write_feather(author.details, 'Data/author_details.feather', compression = 'zstd', compression_level = 5)

```


```{r Exporting institution data, echo = F,eval=T}

dat1 = author.details %>% unnest(author_details) 


dat1 = dat1 %>% 
  filter(country %in% c('India','Switzerland')) %>%
  group_by(institution,country,datasource) %>%
  summarise(nPapers = length(unique(pubNum)), nAuth = length(unique(author)), .groups = 'drop') %>%
  arrange(country,desc(nPapers))

write_csv(dat1,file = 'institutions_for_cleaning_20250417.csv')

dat2 = dat1 %>% 
  mutate(primary_institution = str_split(institution, ",", simplify = TRUE)[,1] %>% str_to_lower())

# Group by primary institution and summarize the data
institution_summary <- dat2 %>%
  group_by(primary_institution, country) %>%
  summarize(
    total_papers = sum(nPapers, na.rm = TRUE),
    total_authors = sum(nAuth, na.rm = TRUE),
    # total_both = sum(nBoth, na.rm = TRUE),
    num_collapsed_inst = n(),
    inst_names = str_c(unique(institution),collapse = '; '),
    .groups = 'drop'
  )
  



```


# Getting data from openAlex

```{r query openAlex, echo = F, eval = F}

# Define the query parameters as a list.
# 'httr' will correctly format these into a URL query string.
# This is where we specify the AND condition for country codes.
library(openalexR)

# Helper function to remove the OpenAlex URL prefix from IDs

clean_id <- function(id) {
  str_remove(id, "(https://openalex.org/)|(https://ror.org/)|(https://doi.org/)|(https://orcid.org/)")
}

get_openalex_data = function(start.date,end.date) {
  query_params <- paste0("https://api.openalex.org/works?",
                       "filter=",
                       "authorships.institutions.country_code:in,",
                  "authorships.institutions.country_code:ch,",
                  "from_publication_date:",start.date,',',
                  "to_publication_date:",end.date,
                  "&select=id,title,display_name,authorships,doi,publication_date,publication_year,primary_location,sources,institution_assertions,countries_distinct_count,institutions_distinct_count,is_authors_truncated,primary_topic,cited_by_count,ids,type,topics,keywords,is_retracted,grants,abstract_inverted_index")


print("Requesting URL from OpenAlex API...")
response <- oa_request(query_url = URLencode(query_params), mailto = 'siddharth.bharath@protonmail.com')

publications_df = oa2df(data = response, entity = 'works')

#Individually get the full authorships data for whichever have truncated records
#Now, any publication with exactly 100 authors is one that has more authors. 
# So we have to query the API to get the information of that single publication

publications_df = mutate(publications_df, rownum = row_number())
auth100 = publications_df %>% filter(map_int(authorships, nrow) == 100) %>% pull(rownum)

if(length(auth100) > 0) {
  for(i in auth100) {
  query_params <- paste0("https://api.openalex.org/works/",clean_id(publications_df$id[i]),"&select=id,authorships")
  response <- oa_request(query_url = query_params)
  x = oa2df(data = response, entity = 'works')$authorships
  publications_df$authorships[i] = x
  rm(x,response)
  if(i%%3 == 0) print(i)
}
}

return(publications_df %>% select(-rownum))

}

publications_df = get_openalex_data(start.date = '2020-01-01',end.date = '2020-01-31')

saveRDS(publications_df,paste0('OA_',start.date,'_',end.date,'.rdata'))


# Process the publications data -------------------------------------------

files = list.files(path = 'Data',pattern = '^OA_.*.rdata$', full.names = T)

publications_df = tibble()

for(i in files) {
  dat = readRDS(i)
  publications_df = bind_rows(publications_df,dat)
  rm(dat)
}

publications_df = publications_df 

# Method 3: Separate main table from nested data (recommended for complex analysis)
# This approach gives you more control over the nested structures

# Extract the main publication data (non-list columns)
main_cols <- publications_df %>%
  select(-authorships, -topics, -keywords, -ids, -grants) %>%
  # Convert any remaining list columns to character if needed
  mutate(across(where(is.list), ~ map_chr(.x, ~ ifelse(is.null(.x), NA_character_, as.character(.x)))))

# Save main publication data
write_parquet(main_cols, "Data/publications_oa_parquet/publications_main.parquet")

# Extract and save nested data separately
# Authorships data
authorships_expanded <- publications_df %>%
  select(id, authorships) %>%
  filter(!map_lgl(authorships, is.null)) %>%
  unnest(authorships) %>%
  # Add publication_id for joining back
  rename(publication_id = id)

write_parquet(authorships_expanded, "Data/publications_oa_parquet/publications_authorships.parquet")

# Topics data
topics_expanded <- publications_df %>%
  select(id, topics) %>%
  filter(!map_lgl(topics, is.null)) %>%
  unnest(topics) %>%
  rename(publication_id = id)

write_parquet(topics_expanded, "publications_topics.parquet")

# Keywords data (handle potential NULL values)
keywords_expanded <- publications_df %>%
  select(id, keywords) %>%
  filter(!map_lgl(keywords, is.null)) %>%
  unnest(keywords) %>%
  rename(publication_id = id)

write_parquet(keywords_expanded, "publications_keywords.parquet")

# IDs data (multiple identifiers per publication)
if (any(!map_lgl(publications_df$ids, is.null))) {
  ids_expanded <- publications_df %>%
    select(id, ids) %>%
    filter(!map_lgl(ids, is.null)) %>%
    unnest_longer(ids) %>%
    rename(publication_id = id, identifier = ids)
  
  write_parquet(ids_expanded, "publications_ids.parquet")
}

# Grants data (if any grants exist)
if (any(!map_lgl(publications_df$grants, is.null))) {
  grants_expanded <- publications_df %>%
    select(id, grants) %>%
    filter(!map_lgl(grants, is.null)) %>%
    unnest(grants) %>%
    rename(publication_id = id)
  
  write_parquet(grants_expanded, "publications_grants.parquet")
}






publications_df = publications_df %>% select(-rownum)
rm(auth100,files)

#Now OpenAlex will miss collaborative publications where the author from India or Switzerland is in the list later than 100.
#So quickly load in the WoS and Scopus data, check all the DOIs that are present there, and not present in openAlex data.
paper.details.ws = readRDS(file = 'Data/publication_details.RData')
ws_dois = tolower(paper.details.ws$doi) #%>% str_c('https://doi.org/')
oa_dois = tolower(publications_df$doi) %>% str_remove('https://doi.org/')
missing_dois = setdiff(ws_dois,oa_dois)

# TODO Now check if these doi entries are in openAlex
missing_dois = paper.details.ws %>% filter(tolower(doi) %in% missing_dois) %>% select(doi,nAuthors)
rm(paper.details.ws)
#First get all those that are with less than 100 authors

dois = missing_dois %>% filter(nAuthors < 100) %>% pull(doi)

# split into batches of 10
batch_size <- 50
doi_batches <- split(dois, ceiling(seq_along(dois) / batch_size))

# fetch in batches and row-bind results
all_works <- purrr::map_dfr(doi_batches, function(batch) {
  # query OpenAlex for these DOIs (entity = "works" returns metadata for publications)
  out <- tryCatch(
    oa_fetch(entity = "works", doi = batch),
    error = function(e) {
      warning("Failed batch: ", paste(batch, collapse = ", "), " → ", e$message)
      tibble()  # return empty on error
    }
  )
  Sys.sleep(0.2)  # small pause to respect API rate limits
  out
})

#Now get the ones that have more than 100 authors

dois = missing_dois %>% filter(nAuthors >= 100) %>% pull(doi)

# split into batches of 10
batch_size  <- 10
doi_batches <- split(dois, ceiling(seq_along(dois) / batch_size))

# fetch only id + doi for each batch, then bind into one tibble
work_ids_tbl <- purrr::map_dfr(doi_batches, function(batch) {
  # small pause to be polite to the API
  Sys.sleep(0.1)
  
  oa_fetch(
    entity  = "works",
    doi     = batch,
    options = list(select = "doi,id")
  ) %>%
    select(doi, id)
})

#check all_works - if any of the entries have exactly 100 authors, then add them to work_ids_tbl

nauth = all_works %>% 
  filter(map_int(authorships, nrow) == 100) %>% select(id,doi)
all_works = all_works %>% filter(map_int(authorships, nrow) != 100)


for(i in 1:nrow(work_ids_tbl)) {
  query_params <- paste0("https://api.openalex.org/works/",clean_id(work_ids_tbl$id[i]),"?mailto=siddharth.bharath@protonmail.com,")
  response <- oa_request(query_url = query_params)
  x = oa2df(data = response, entity = 'works')
  all_works = bind_rows(all_works,x)
  rm(x,response)
  if(i%%3 == 0) print(i)
}

saveRDS(all_works, 'Data/Additional_openAlex.rdata')

publications_df = bind_rows(publications_df,all_works) %>%
  group_by(id) %>% slice_tail(n = 1) %>%
  select(-concepts,-apc,-referenced_works,-related_works,-referenced_works_count, -landing_page_url,-counts_by_year)

# big_works = readRDS('Data/Additional_openAlex_big.rdata')

saveRDS(publications_df, 
        'Data/openAlex_df_2000-2024.rdata')

#creating a schema for saving it in Arrow
# 1. A quick “glimpse” of top-level classes
dplyr::glimpse(publications_df)

# 2. A table of each column’s R class
tibble(
  name          = names(publications_df),
  top_class     = map_chr(publications_df, ~ paste(class(.), collapse="/"))
)

# 3. For list-columns, what’s inside the first element?
list_cols <- names(publications_df)[purrr::map_lgl(publications_df, is.list)]
purrr::map(publications_df[list_cols], ~ class(.x[[1]]) )

# 4. (If you have nested tibbles) for each list-column that’s a data‐frame:
purrr::map(publications_df[list_cols], ~ if (inherits(.x[[1]], "data.frame")) str(.x[[1]]))

#Some entries are missing the Authorship data correctly. So replace those with a 0 x 7 dataframe
proto <- publications_df$authorships %>% 
  keep(~ is.data.frame(.x) && ncol(.x) > 0) %>% 
  first()

# 2) Make an empty version (0 rows, same columns & types)
proto_empty <- proto[0, ]

# 3) Replace every 0×0 authorships with that empty prototype
publications_df <- publications_df %>%
  mutate(
    authorships = map(authorships, ~ {
      if (is.data.frame(.x) && ncol(.x) == 0) {
        proto_empty
      } else {
        .x
      }
    })
  )

# 2) Define the full Arrow schema
my_schema <- schema(
  id                          = utf8(),
  title                       = utf8(),
  display_name                = utf8(),
  authorships                 = list_of(
    struct(
      id                   = utf8(),
      display_name         = utf8(),
      # orcid                = utf8(),
      author_position      = utf8(),
      is_corresponding     = bool(),
      affiliations         = list_of(
        struct(
          id              = utf8(),
          display_name    = utf8(),
          ror             = utf8(),
          country_code    = utf8(),
          type            = utf8(),
          lineage         = utf8()
        )
      ),
      affiliation_raw      = utf8()
    )
  ),
  abstract                    = utf8(),
  doi                         = utf8(),
  publication_date            = date32(),    # days-since-1970
  publication_year            = int32(),
  fwci                        = float64(),
  cited_by_count              = int32(),
  cited_by_api_url            = utf8(),
  ids                         = list_of(utf8()),
  type                        = utf8(),
  is_oa                       = bool(),
  is_oa_anywhere              = bool(),
  oa_status                   = utf8(),
  oa_url                      = utf8(),
  any_repository_has_fulltext = bool(),
  source_display_name         = utf8(),
  source_id                   = utf8(),
  issn_l                      = utf8(),
  host_organization           = utf8(),
  host_organization_name      = utf8(),
  pdf_url                     = utf8(),
  license                     = utf8(),
  version                     = utf8(),
  topics                      = list_of(
    struct(
      i               = int32(),
      score           = float64(),
      id              = utf8(),
      display_name    = utf8(),
      type            = utf8()
    )
  ),
  keywords                    = list_of(
    struct(
      id              = utf8(),
      display_name    = utf8(),
      score           = float64()
    )
  ),
  is_paratext                 = bool(),
  is_retracted                = bool(),
  language                    = utf8(),
  grants                      = list_of(utf8()),
  first_page                  = utf8(),
  last_page                   = utf8(),
  volume                      = utf8(),
  issue                       = utf8()
)

publications_df <- publications_df %>%
  mutate(
    authorships = map(authorships, ~
      # for each tibble of authors, drop the orcid column
      .x %>% select(-orcid)
    )
  )

# 3) Create an Arrow Table with that schema
tbl <- Table$create(publications_df, schema = my_schema)

# 4) Write out a segmented Parquet dataset
write_dataset(tbl, "metadata_parquet/", format = "parquet")



write_dataset(publications_df, 'Data/publications_oa_parquet/', format = 'parquet')


```


```{r Process openAlex, echo = F}

# dat_authors = publications_df %>%
#   select(work_id = id,work_title = display_name, authorships) %>%
#   unnest(cols = 'authorships',names_repair = 'unique') %>% 
#   rename(author_id = id, author_name = display_name) %>%
#   unnest(cols = 'affiliations') %>%
#   rename(inst_id = id, inst_name = display_name)

publications_df = readRDS('Data/openAlex_df_2000-2024.rdata')



# The core of the work is to process the 'authorships' list-column.
# We'll create a new set of columns with author and institution statistics.
processed_data <- publications_df %>% slice_sample(n=10) %>%
  # Add a unique publication number for easy reference, similar to pubNum in the Rmd
  mutate(pubNum = row_number(), work_id = clean_id(id)) %>%
  select(-id) %>%
  # Create a new column that processes the authorships for each paper
  mutate(
    # 'map' iterates through the 'authorships' column for each publication
    author_info = map(authorships,function(authors_df) {
      # Unnest the affiliations for each author. This is the key step.
      # Each row will now be one author affiliated with one institution for that paper.
      author_inst <- authors_df %>%
        mutate(author_id = clean_id(id), orcid= str_remove(orcid,"https://orcid.org/")) %>%
        select(author_id, author_name = display_name, orcid, affiliations) %>%
        unnest(affiliations, keep_empty = TRUE) %>%
        mutate(inst_id = clean_id(id), ror = str_remove(ror,'https://ror.org/')) %>%
        select(author_id, orcid, author_name, inst_name = display_name, inst_id, ror, country_code)
      
      author_inst %>% nest(institutions = any_of(c('inst_name', 'inst_id', 'ror', 'country_code')))
      
    })) %>%
  select(-authorships) %>%
  mutate(author_stats = map(author_info, function(authors_df) {

      # If there are no authors, return an empty summary
      if (is.null(authors_df) || nrow(authors_df) == 0) {
        return(
          tibble(
            nAuthors = 0, nIndAuth = 0, nSwissAuth = 0, nBothAuth = 0,
            nIndInst = 0, nSwissInst = 0, nCountries = 0
          )
        )
      }
    authors_df = authors_df %>% unnest(institutions) 
    # For each author on the paper, find all their unique country codes
    author_countries <- authors_df %>%
      group_by(author_id, author_name) %>%
      summarise(
        countries = list(unique(country_code)),
        .groups = 'drop'
      ) %>%
      # Categorize each author based on their affiliations for this paper
      mutate(
        is_swiss = map_lgl(countries, ~ "CH" %in% .x),
        is_indian = map_lgl(countries, ~ "IN" %in% .x),
        auth_cat = case_when(
          is_swiss & is_indian ~ "Both",
          is_swiss ~ "Swiss",
          is_indian ~ "India",
          TRUE ~ "Other"
        )
      )
    
      # Calculate the summary statistics for the single publication
      tibble(
        nAuthors = n_distinct(author_countries$author_id),
        nIndAuth = sum(author_countries$auth_cat == "India"),
        nSwissAuth = sum(author_countries$auth_cat == "Swiss"),
        nBothAuth = sum(author_countries$auth_cat == "Both"),
        nIndInst = n_distinct(authors_df$inst_name[authors_df$country_code == "IN"], na.rm = TRUE),
        nSwissInst = n_distinct(authors_df$inst_name[authors_df$country_code == "CH"], na.rm = TRUE),
        nCountries = n_distinct(authors_df$country_code, na.rm = TRUE)
      )
    }),
    topic_info = map(topics, function(topics_df) {
      # --- Process Topic Data ---
      top_topic_info <- list( # Default empty list
        topic = tibble(id=NA, display_name=NA),
        subfield = tibble(id=NA, display_name=NA),
        field = tibble(id=NA, display_name=NA),
        domain = tibble(id=NA, display_name=NA)
      )
      
      if (!is.null(topics_df) && nrow(topics_df) > 0) {
        # The highest-ranked topic is the first one in the list
        top_topic <- topics_df %>% mutate(id = clean_id(id)) %>%
          pivot_wider(names_from = type,values_from = id:display_name, names_sep = '.') %>%
          rename(topic_rank = i,topic_class_score = score, topic.id = id.topic, subfield.id = id.subfield, field.id = id.field, domain.id = id.domain,
                 topic.name = display_name.topic, subfield.name = display_name.subfield,field.name = display_name.field,domain.name = display_name.domain) %>%
          as_tibble()
        return(top_topic)
      }
    })
  ) %>%
  # select(-topics) %>%
  # Unnest the new 'author_stats' column to make them regular columns
  unnest(author_stats) %>%
  select(-topics)

ntopics = publications_df %>%
  select(id, topics, authorships) %>% 
  mutate(topics_rows = map_int(topics, function(topics_df) {nrow(topics_df)}),
         nauth = map_int(authorships, function(topics_df) {nrow(topics_df)}))

saveRDS(processed_data,file = 'openAlex_processed.rdata')

write_feather(processed_data, 
              'Data/openAlex_df_2000-2024.feather', compression = 'zstd', compression_level = 5)


# --- 4. CREATE FINAL OUTPUT FILES ---
# Recreate the two main data frames as in the WoS + Scopus analysis



# 4a. paper.details: One row per publication with summary stats
paper.details <- processed_data %>%
  select(
    pubNum,
    work_id,
    doi,
    title,
    abstract,
    document_type = type,
    publication_year,
    language,
    source_title = source_display_name,
    is_oa,
    # grants,
    oa_status,
    cited_by_count,
    fwci,
    is_retracted,
    topic_info,
    # Add the newly created summary stats
    nAuthors, nIndAuth, nSwissAuth, nBothAuth, nIndInst, nSwissInst, nCountries
  ) %>%
  unnest(topic_info) %>% group_by(pubNum) %>% slice_head(n = 1) %>%
  select(-topic_rank,-topic_class_score,-topic.id,-subfield.id,-field.id,-domain.id) %>%
  # Add a datasource column for consistency
  mutate(datasource = "OpenAlex")

# 4b. author.details: Contains the nested data for deeper author analysis
author.details <- processed_data %>%
  select(pubNum,work_id, author_info, nAuthors:nCountries) %>%
  mutate(datasource = "OpenAlex")


# --- 5. DISPLAY AND SAVE RESULTS ---

print("--- Publication Details (paper.details) ---")
glimpse(paper.details)

print("--- Author Details (author.details) ---")
glimpse(author.details)

write_feather(paper.details, 
              'Data/openAlex_paper_details_flat.feather', compression = 'zstd', compression_level = 5)

write_feather(author.details, 
              'Data/openAlex_author_details.feather', compression = 'zstd', compression_level = 5)


```


```{r Combine OpenAlex, Scopus and WoS data}

paper.details.oa = read_feather('Data/openAlex_paper_details_flat.feather')

paper.details.oa = filter(paper.details.oa,!is_retracted) %>% select(-is_retracted)

paper.details.oa = paper.details.oa %>% filter(document_type %in% c('article','book','book-chapter','dataset','letter','reference-entry','report','review', 'editorial')) %>% ungroup() %>%
  mutate(doi = tolower(str_remove(doi,"https://doi.org/"))) %>%
  select(-pubNum) %>% rename(publication_year = year)

paper.details.ws = readRDS(file = 'Data/publication_details.RData')

paper.details.ws = paper.details.ws %>% filter((grepl('(Article|Review|Book)',`document type`) | `document type` %in% c('Conference paper','Data paper','Proceedings Paper', 'Review', 'Short survey','Editorial')) & !grepl('Retract', `document type`)) %>%
  select(-pubNum)

#Combine the two datasets - paper.details.ws and paper.details.oa
#the unique id for a paper is the DOI
#Prefer the abstract, title, year, 

```


<!-- Chunks that are not current priorities -->



```{r Matching those without doi, echo = F, eval=F}


printo('For the WoS data, ',sum(is.na(wosdat$doi)), " out of ", nrow(wosdat), ' entries do not have a doi. These are books or conference proceedings.')

wos.nodoi = wosdat %>% filter(is.na(doi))
#how many of these have unique ISSN or ISBN
wos.isbn = wos.nodoi %>% filter(!is.na(ISBN)) %>% group_by(ISBN) %>% summarise(count = n()) %>% arrange(desc(count))
table(wos.isbn$count)
wos.issn = wos.nodoi %>% filter(!is.na(ISSN)) %>% group_by(ISSN) %>% summarise(count = n()) %>% arrange(desc(count))



```


