---
title: "Summary of Publications Dataset"
author: "Siddharth Bharath, Pranshu Jaiswal, Lena Robra, Manfred Max Bergman"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    theme: flatly
    highlight: tango
  pdf_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.width = 10, fig.height = 6)
library(dplyr)
library(ggplot2)
library(plotly)
library(DT)
library(scales)
library(kableExtra)
library(tidyr)
library(lubridate)
library(stringr)
library(arrow)

paper.details.oa.final <- read_parquet("Data/publications_compiled_2000-2024.parquet")
```

# Executive Summary

This report provides a comprehensive overview of our enhanced research publication dataset, combining data from **OpenAlex**, **Web of Science**, and **Scopus**. The dataset has been comprehensively enhanced with abstracts, citation counts, funding information, and keyword data from multiple sources.

```{r overview-stats}
# Generate key statistics
total_papers <- nrow(paper.details.oa.final)
date_range <- range(paper.details.oa.final$publication_date, na.rm = TRUE)
year_range <- range(paper.details.oa.final$publication_year, na.rm = TRUE)

# Data completeness
papers_with_abstracts <- sum(!is.na(paper.details.oa.final$abstract) & paper.details.oa.final$abstract != "")
papers_with_citations <- sum(!is.na(paper.details.oa.final$cited_by_count) & paper.details.oa.final$cited_by_count > 0)
papers_with_topics <- sum(!is.na(paper.details.oa.final$primary_topic_name))
papers_with_funding <- sum(!is.na(paper.details.oa.final$funding_details) & paper.details.oa.final$funding_details != "")
papers_openaccess <- sum(paper.details.oa.final$is_oa, na.rm = TRUE)

# Create summary table
overview_stats <- data.frame(
  Metric = c("Total Publications", "Date Range", "Papers with Abstracts", 
             "Papers with Citations", "Papers with OpenAlex Topics", 
             "Papers with Funding Info", "Open Access Papers"),
  Value = c(
    comma(total_papers),
    paste(format(date_range[1], "%Y"), "-", format(date_range[2], "%Y")),
    paste0(comma(papers_with_abstracts), " (", round(100*papers_with_abstracts/total_papers, 1), "%)"),
    paste0(comma(papers_with_citations), " (", round(100*papers_with_citations/total_papers, 1), "%)"),
    paste0(comma(papers_with_topics), " (", round(100*papers_with_topics/total_papers, 1), "%)"),
    paste0(comma(papers_with_funding), " (", round(100*papers_with_funding/total_papers, 1), "%)"),
    paste0(comma(papers_openaccess), " (", round(100*papers_openaccess/total_papers, 1), "%)")
  )
)

kable(overview_stats, caption = "Dataset Overview") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
```

---

# Data Sources and Coverage

## Database Coverage Analysis

```{r coverage-analysis, fig.height=8}
# Recreate coverage analysis for the final dataset
# Note: This assumes you have the original coverage data
# You may need to adapt this based on your actual data structure

# Create a simple coverage summary
source_summary <- data.frame(
  Source = c("OpenAlex", "Web of Science + Scopus", "Combined Enhanced"),
  Papers = c(24907, 69, total_papers),
  Coverage = c("Primary source", "Additional papers", "Final dataset")
)

# Visualize data sources
p1 <- ggplot(source_summary, aes(x = Source, y = Papers, fill = Source)) +
  geom_col(alpha = 0.8, width = 0.6) +
  geom_text(aes(label = comma(Papers)), vjust = -0.5, fontface = "bold") +
  scale_fill_brewer(type = "qual", palette = "Set2") +
  scale_y_continuous(labels = comma_format(), expand = expansion(mult = c(0, 0.1))) +
  labs(title = "Data Source Contribution",
       subtitle = "Number of papers from each source",
       x = "Data Source", y = "Number of Papers") +
  theme_minimal() +
  theme(legend.position = "none",
        plot.title = element_text(size = 14, face = "bold"))

print(p1)
```

---

# Temporal Distribution

## Publication Timeline

```{r temporal-analysis}
# Annual publication trends
annual_pubs <- paper.details.oa.final %>%
  filter(!is.na(publication_year) & publication_year >= 1990) %>%
  count(publication_year) %>%
  arrange(publication_year)

# Plot publication timeline
p2 <- ggplot(annual_pubs, aes(x = publication_year, y = n)) +
  geom_line(color = "#2E8B57", size = 1.2) +
  geom_point(color = "#2E8B57", size = 2) +
  scale_x_continuous(breaks = seq(1990, 2025, 5)) +
  scale_y_continuous(labels = comma_format()) +
  labs(title = "Publication Timeline",
       subtitle = paste("Publications per year (", min(annual_pubs$publication_year), "-", max(annual_pubs$publication_year), ")"),
       x = "Publication Year", y = "Number of Publications") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

print(p2)

# Key temporal statistics
peak_year <- annual_pubs$publication_year[which.max(annual_pubs$n)]
peak_count <- max(annual_pubs$n)
recent_5_years <- sum(annual_pubs$n[annual_pubs$publication_year >= (max(annual_pubs$publication_year) - 4)])

cat("**Temporal Insights:**\n")
cat("- Peak publication year:", peak_year, "with", comma(peak_count), "papers\n")
cat("- Publications in last 5 years:", comma(recent_5_years), "\n")
cat("- Average publications per year:", round(mean(annual_pubs$n), 1), "\n")
```

---

# Research Topics and Domains

## Topic Distribution

```{r topic-analysis, fig.height=10}
# Top research domains
domain_analysis <- paper.details.oa.final %>%
  filter(!is.na(primary_domain_name)) %>%
  count(primary_domain_name, sort = TRUE) %>%
  mutate(percentage = round(100 * n / sum(n), 1))

# Top research fields
field_analysis <- paper.details.oa.final %>%
  filter(!is.na(primary_field_name)) %>%
  count(primary_field_name, sort = TRUE) %>%
  head(15) %>%
  mutate(percentage = round(100 * n / sum(n), 1))

# Top research topics
topic_analysis <- paper.details.oa.final %>%
  filter(!is.na(primary_topic_name)) %>%
  count(primary_topic_name, sort = TRUE) %>%
  head(20) %>%
  mutate(
    percentage = round(100 * n / sum(n), 1),
    primary_topic_name = str_wrap(primary_topic_name, 40)
  )

# Plot domains
p3 <- ggplot(domain_analysis, aes(x = reorder(primary_domain_name, n), y = n, fill = primary_domain_name)) +
  geom_col(alpha = 0.8) +
  geom_text(aes(label = paste0(comma(n), "\n(", percentage, "%)")), hjust = -0.1, size = 3.5) +
  scale_y_continuous(labels = comma_format(), expand = expansion(mult = c(0, 0.15))) +
  coord_flip() +
  labs(title = "Research Domains Distribution",
       x = "Domain", y = "Number of Papers") +
  theme_minimal() +
  theme(legend.position = "none")

# Plot top fields
p4 <- ggplot(field_analysis, aes(x = reorder(primary_field_name, n), y = n, fill = primary_field_name)) +
  geom_col(alpha = 0.8) +
  geom_text(aes(label = paste0(comma(n), "\n(", percentage, "%)")), hjust = -0.1, size = 3) +
  scale_y_continuous(labels = comma_format(), expand = expansion(mult = c(0, 0.15))) +
  coord_flip() +
  labs(title = "Top 15 Research Fields",
       x = "Field", y = "Number of Papers") +
  theme_minimal() +
  theme(legend.position = "none",
        axis.text.y = element_text(size = 10))

# Plot top topics
p5 <- ggplot(topic_analysis, aes(x = reorder(primary_topic_name, n), y = n, fill = primary_topic_name)) +
  geom_col(alpha = 0.8) +
  geom_text(aes(label = comma(n)), hjust = -0.1, size = 3) +
  scale_y_continuous(labels = comma_format(), expand = expansion(mult = c(0, 0.1))) +
  coord_flip() +
  labs(title = "Top 20 Research Topics",
       x = "Topic", y = "Number of Papers") +
  theme_minimal() +
  theme(legend.position = "none",
        axis.text.y = element_text(size = 9))

print(p3)
print(p4)
print(p5)
```

## Topic Summary Tables

```{r topic-tables}
# Domain summary
kable(domain_analysis, 
      col.names = c("Research Domain", "Papers", "Percentage"),
      caption = "Research Domain Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

# Field summary (top 10)
kable(head(field_analysis, 10), 
      col.names = c("Research Field", "Papers", "Percentage"),
      caption = "Top 10 Research Fields") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
```

---

# Citation Impact Analysis

## Citation Distribution

```{r citation-analysis}
# Citation statistics
citation_stats <- paper.details.oa.final %>%
  filter(!is.na(cited_by_count)) %>%
  summarise(
    total_papers = n(),
    total_citations = sum(cited_by_count),
    mean_citations = round(mean(cited_by_count), 1),
    median_citations = median(cited_by_count),
    max_citations = max(cited_by_count),
    highly_cited = sum(cited_by_count >= 100),
    uncited = sum(cited_by_count == 0)
  )

# Citation distribution plot
citation_dist <- paper.details.oa.final %>%
  filter(!is.na(cited_by_count) & cited_by_count <= 1000) %>%
  ggplot(aes(x = cited_by_count)) +
  geom_histogram(bins = 50, fill = "#3498db", alpha = 0.7) +
  scale_x_continuous(labels = comma_format()) +
  scale_y_continuous(labels = comma_format()) +
  labs(title = "Citation Distribution",
       subtitle = "Papers with ≤1000 citations (for visualization clarity)",
       x = "Citations", y = "Number of Papers") +
  theme_minimal()

print(citation_dist)

# Most cited papers
most_cited <- paper.details.oa.final %>%
  filter(!is.na(cited_by_count)) %>%
  arrange(desc(cited_by_count)) %>%
  head(10) %>%
  select(title, cited_by_count, publication_year, primary_topic_name) %>%
  mutate(
    title = str_trunc(title, 60),
    primary_topic_name = str_trunc(primary_topic_name, 30)
  )

# Citation statistics table
citation_summary <- data.frame(
  Metric = c("Total Citations", "Mean Citations", "Median Citations", 
             "Max Citations", "Highly Cited (≥100)", "Uncited Papers"),
  Value = c(
    comma(citation_stats$total_citations),
    citation_stats$mean_citations,
    citation_stats$median_citations,
    comma(citation_stats$max_citations),
    paste0(comma(citation_stats$highly_cited), " (", round(100*citation_stats$highly_cited/citation_stats$total_papers, 1), "%)"),
    paste0(comma(citation_stats$uncited), " (", round(100*citation_stats$uncited/citation_stats$total_papers, 1), "%)")
  )
)

kable(citation_summary, caption = "Citation Impact Statistics") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

kable(most_cited, 
      col.names = c("Title", "Citations", "Year", "Primary Topic"),
      caption = "Top 10 Most Cited Papers") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
```

---

# Data Quality and Completeness

## Completeness Analysis

```{r completeness-analysis}
# Data completeness assessment
completeness <- paper.details.oa.final %>%
  summarise(
    abstracts = round(100 * sum(!is.na(abstract) & abstract != "") / n(), 1),
    citations = round(100 * sum(!is.na(cited_by_count)) / n(), 1),
    topics = round(100 * sum(!is.na(primary_topic_name)) / n(), 1),
    funding = round(100 * sum(!is.na(funding_details) & funding_details != "") / n(), 1),
    keywords_author = round(100 * sum(!is.na(author_keywords) & author_keywords != "") / n(), 1),
    keywords_scopus = round(100 * sum(!is.na(index_keywords_scopus) & index_keywords_scopus != "") / n(), 1),
    keywords_wos = round(100 * sum(!is.na(keywords_plus_wos) & keywords_plus_wos != "") / n(), 1),
    dois = round(100 * sum(!is.na(doi) & doi != "") / n(), 1),
    open_access = round(100 * sum(!is.na(is_oa)) / n(), 1)
  ) %>%
  pivot_longer(everything(), names_to = "Field", values_to = "Completeness") %>%
  mutate(
    Field = case_when(
      Field == "abstracts" ~ "Abstracts",
      Field == "citations" ~ "Citations",
      Field == "topics" ~ "OpenAlex Topics",
      Field == "funding" ~ "Funding Details",
      Field == "keywords_author" ~ "Author Keywords",
      Field == "keywords_scopus" ~ "Scopus Keywords",
      Field == "keywords_wos" ~ "WoS Keywords",
      Field == "dois" ~ "DOIs",
      Field == "open_access" ~ "Open Access Status"
    )
  ) %>%
  arrange(desc(Completeness))

# Plot completeness
completeness_plot <- ggplot(completeness, aes(x = reorder(Field, Completeness), y = Completeness, fill = Field)) +
  geom_col(alpha = 0.8) +
  geom_text(aes(label = paste0(Completeness, "%")), hjust = -0.1, fontface = "bold") +
  scale_y_continuous(limits = c(0, 105), expand = expansion(mult = c(0, 0))) +
  coord_flip() +
  labs(title = "Data Completeness by Field",
       subtitle = "Percentage of papers with non-missing data",
       x = "Data Field", y = "Completeness (%)") +
  theme_minimal() +
  theme(legend.position = "none")

print(completeness_plot)

kable(completeness, 
      col.names = c("Data Field", "Completeness (%)"),
      caption = "Data Completeness Summary") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
```

---

# Enhanced Data Features

## Funding Information Analysis

```{r funding-analysis}
# Funding information statistics
funding_stats <- paper.details.oa.final %>%
  summarise(
    papers_with_funding = sum(!is.na(funding_details) & funding_details != ""),
    papers_with_funding_text = sum(!is.na(funding_text) & funding_text != ""),
    original_grants = sum(!is.na(grants) & grants != ""),
    total_papers = n()
  ) %>%
  mutate(
    funding_improvement = papers_with_funding - original_grants,
    funding_coverage = round(100 * papers_with_funding / total_papers, 1)
  )

funding_summary <- data.frame(
  Metric = c("Original OpenAlex Grants", "Enhanced Funding Details", "Enhanced Funding Text", 
             "Funding Coverage", "Improvement"),
  Value = c(
    comma(funding_stats$original_grants),
    comma(funding_stats$papers_with_funding),
    comma(funding_stats$papers_with_funding_text),
    paste0(funding_stats$funding_coverage, "%"),
    paste0("+", comma(funding_stats$funding_improvement), " papers")
  )
)

kable(funding_summary, caption = "Funding Information Enhancement") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
```

## Keywords Enhancement

```{r keywords-analysis}
# Keywords statistics
keywords_stats <- paper.details.oa.final %>%
  summarise(
    author_kw = sum(!is.na(author_keywords) & author_keywords != ""),
    scopus_kw = sum(!is.na(index_keywords_scopus) & index_keywords_scopus != ""),
    wos_kw = sum(!is.na(keywords_plus_wos) & keywords_plus_wos != ""),
    original_kw = sum(!is.na(keywords) & keywords != ""),
    total_papers = n()
  )

keywords_summary <- data.frame(
  Keyword_Type = c("Original OpenAlex Keywords", "Author Keywords", "Scopus Index Keywords", "WoS Keywords Plus"),
  Papers = c(keywords_stats$original_kw, keywords_stats$author_kw, 
             keywords_stats$scopus_kw, keywords_stats$wos_kw),
  Coverage = c(
    round(100 * keywords_stats$original_kw / keywords_stats$total_papers, 1),
    round(100 * keywords_stats$author_kw / keywords_stats$total_papers, 1),
    round(100 * keywords_stats$scopus_kw / keywords_stats$total_papers, 1),
    round(100 * keywords_stats$wos_kw / keywords_stats$total_papers, 1)
  )
) %>%
  mutate(Coverage = paste0(Coverage, "%"))

kable(keywords_summary, 
      col.names = c("Keyword Type", "Papers", "Coverage"),
      caption = "Keywords Coverage by Source") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
```

---

# Document Types and Open Access

## Document Type Distribution

```{r document-types}
# Document types
doc_types <- paper.details.oa.final %>%
  count(`document type`, sort = TRUE) %>%
  mutate(percentage = round(100 * n / sum(n), 1)) %>%
  filter(!is.na(`document type`))

doc_plot <- ggplot(doc_types, aes(x = reorder(`document type`, n), y = n, fill = `document type`)) +
  geom_col(alpha = 0.8) +
  geom_text(aes(label = paste0(comma(n), "\n(", percentage, "%)")), hjust = -0.1, size = 3.5) +
  scale_y_continuous(labels = comma_format(), expand = expansion(mult = c(0, 0.15))) +
  coord_flip() +
  labs(title = "Document Type Distribution",
       x = "Document Type", y = "Number of Papers") +
  theme_minimal() +
  theme(legend.position = "none")

print(doc_plot)

# Open Access analysis
oa_analysis <- paper.details.oa.final %>%
  filter(!is.na(is_oa)) %>%
  count(is_oa) %>%
  mutate(
    status = ifelse(is_oa, "Open Access", "Not Open Access"),
    percentage = round(100 * n / sum(n), 1)
  )

kable(oa_analysis %>% select(status, n, percentage), 
      col.names = c("Access Type", "Papers", "Percentage"),
      caption = "Open Access Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
```

---

# Key Insights for Future Analysis

## Dataset Strengths

- **Comprehensive Coverage**: `r comma(total_papers)` publications from multiple authoritative sources
- **High Citation Data**: `r round(100*papers_with_citations/total_papers, 1)`% of papers have citation information
- **Rich Topic Classification**: `r round(100*papers_with_topics/total_papers, 1)`% have OpenAlex topic assignments
- **Enhanced Abstracts**: `r round(100*papers_with_abstracts/total_papers, 1)`% coverage after enhancement
- **Multiple Keyword Sources**: Three different keyword classification systems available

## Analytical Opportunities

1. **Temporal Analysis**: Publications span `r year_range[2] - year_range[1]` years with clear growth patterns
2. **Domain Comparison**: Well-distributed across `r nrow(domain_analysis)` major