---
title: "Indo-Swiss Research Database - Merging data available between Web of Science,
  Scopus and OpenAlex"
author: "Siddharth Bharath, Pranshu Jaiswal, Lena Robra, Manfred Max Bergman"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
  always_allow_html: true
  word_document: default
---

This report presents the comprehensive results of a multi-phase data enhancement and processing exercise that successfully created the most complete dataset of Indo-Swiss collaborative research publications available. The project integrated publication metadata from three major bibliographic databases (OpenAlex, Web of Science, and Scopus) and performed extensive author and institutional data processing to create a structured, analysis-ready research collaboration database.
Database Coverage and Integration
The final enhanced dataset contains 24,979 unique publications, representing a substantial expansion from the original Phase 1 database. The coverage analysis reveals the complementary nature of the three databases:
Individual Database Coverage

OpenAlex: 24,900 DOIs (99.7% coverage) - highest overall coverage
Scopus: 16,546 DOIs (66.2% coverage)
Web of Science: 16,058 DOIs (64.3% coverage)

Coverage Overlap Analysis

Unique to one database: 5,892 DOIs (23.6% of total)
OpenAlex-only publications: 79 papers that could not be matched to WoS/Scopus

The high OpenAlex coverage (99.7%) demonstrates the value of incorporating this open-access focused database, which captured nearly 5,900 additional publications beyond what was available through traditional subscription databases alone.
Data Enhancement Results
The integration process significantly improved data completeness across multiple critical fields:
Abstract Enhancement

Original abstracts (OpenAlex only): 18,434 papers
Enhanced abstracts: 22,929 papers
Improvement: 4,495 additional abstracts (+24.4%)

Citation Data Enhancement

Original citations: 20,973 papers
Enhanced citations: 21,264 papers
Improvement: 291 additional citation records

Funding Information Enhancement
This represents the most significant improvement in data completeness:

Original funding records (OpenAlex): 5,345 papers
Enhanced funding details: 13,234 papers
Enhanced funding text: 12,419 papers
Total improvement: 7,889 additional funding records (+147.6%)

Keywords and Topic Classification

Author keywords: Comprehensive coverage with 23,945 papers from OpenAlex plus 10,313 from WoS/Scopus
Scopus index keywords: 11,716 papers
Web of Science Keywords Plus: 12,937 papers
OpenAlex topic classification: 24,392 papers (97.6% coverage)

Author and Institution Processing
Processing Scale and Performance
A comprehensive processing operation handled 5.4 million individual author-publication records, involving:

82,284 unique JSON affiliation records parsed and standardized
Complete processing time: Approximately 7 minutes for the entire pipeline
Zero data loss during aggregation and deduplication

Author-Level Processing (5.4M records)

Institution standardization: Extracted clean institution names with country codes (format: "Institution Name, CC")
Multiple affiliation handling: Properly processed authors with multiple institutional affiliations
Country extraction: Identified all countries associated with each author
Quantitative metrics: Added counts of institutions and countries per author

Publication-Level Aggregation (24,979 publications)

Deduplication: Ensured unique institution lists per publication (no repeated institutions)
Comprehensive coverage: 97.0% of publications (24,013) have complete institutional data
Geographic mapping: 97.0% of publications have country information
Author consolidation: Combined all authors per publication with complete affiliation details

Institutional Landscape Analysis
The processing identified 2,250 unique institutions from India and Switzerland, revealing the collaborative research ecosystem:
Top Collaborative Institutions:

ETH Zurich (CH): 3,448 publications, 3,274 authors
University of Zurich (CH): 2,834 publications, 2,257 authors
European Organization for Nuclear Research (CH): 2,802 publications, 8,693 authors
Tata Institute of Fundamental Research (IN): 2,553 publications, 888 authors
Panjab University (IN): 2,494 publications, 413 authors

Key Achievements

Comprehensive Coverage: Achieved 99.7% database coverage through OpenAlex integration
Enhanced Metadata Quality: Significant improvements in abstracts (+24.4%) and funding information (+147.6%)
Multi-Source Validation: Three-database approach enables cross-validation and gap-filling
Advanced Topic Classification: OpenAlex's machine learning-based topic classification covers 97.6% of publications
Institutional Mapping: Processed 2,250 unique institutions with complete relationship networks
Open Science Alignment: Integration with OpenAlex supports open science principles while maintaining quality

Final Dataset Characteristics
The enhanced dataset contains:

Total publications: 24,979
Publications with abstracts: 22,929 (91.8%)
Publications with citations: 21,264 (85.1%)
Publications with funding information: 13,234 (53.0%)
Publications with topic classification: 24,392 (97.6%)
Publications with institutional data: 24,013 (97.0%)

Data Products Delivered
Three optimized datasets were created in Parquet format for efficient analysis:

Flat Author Dataset: 5.4M records with individual author-institution mappings
Publication Summary: 24,979 publications with aggregated metadata
Institutional Relationships: 2,250 institutions with linked publication networks

Strategic Impact
This comprehensive enhancement represents a significant advancement in the scope and analytical potential of the Indo-Swiss research collaboration database. The multi-database approach combined with extensive processing has resulted in:

23.6% increase in unique publications discovered
Near-complete coverage (99.7%) of the collaborative research landscape
Dramatically improved funding information for policy analysis
Advanced topic classification capabilities for trend analysis
Enhanced research impact assessment through improved citation data
Relational database readiness for institutional collaboration analysis

The resulting database now provides stakeholders with the most comprehensive view of Indo-Swiss research collaborations available, supporting evidence-based policy decisions, strategic research planning, and detailed bibliometric analysis of bilateral scientific cooperation.

---

## Appendix A: Final Dataset Field Descriptions

| Field Name | Description |
|------------|-------------|
| `work_id` | OpenAlex unique work identifier |
| `title` | Publication title (harmonized across databases) |
| `display_name` | Display name from OpenAlex |
| `abstract` | Abstract text (enhanced from multiple sources) |
| `doi` | Digital Object Identifier |
| `publication_date` | Full publication date |
| `publication_year` | Publication year (integer) |
| `cited_by_count` | Citation count (maximum from all databases) |
| `ids` | JSON array of all identifiers across databases |
| `document type` | Document type classification (normalized to lowercase) |
| `is_oa` | Open access status (boolean) |
| `source_display_name` | Journal/venue name |
| `source_id` | OpenAlex source identifier |
| `issn_l` | Linking ISSN |
| `host_organization` | Publisher organization ID |
| `host_organization_name` | Publisher organization name |
| `landing_page_url` | Primary URL for the publication |
| `pdf_url` | Direct PDF access URL (when available) |
| `license` | Publication license information |
| `version` | Publication version type |
| `keywords` | OpenAlex keyword classification (JSON) |
| `is_retracted` | Retraction status (boolean) |
| `grants` | Grant information from OpenAlex |
| `primary_topic_id` | Primary research topic ID (OpenAlex classification) |
| `primary_topic_name` | Primary research topic name |
| `primary_topic_score` | Topic classification confidence (0-1) |
| `primary_subfield_id` | Research subfield ID |
| `primary_subfield_name` | Research subfield name |
| `primary_field_id` | Research field ID |
| `primary_field_name` | Research field name |
| `primary_domain_id` | Research domain ID |
| `primary_domain_name` | Research domain name |
| `funding_details` | Enhanced funding details (from WoS/Scopus) |
| `funding_text` | Enhanced funding acknowledgment text |
| `author_keywords` | Author-provided keywords (enhanced) |
| `index_keywords_scopus` | Scopus-assigned index keywords |
| `keywords_plus_wos` | Web of Science Keywords Plus |

**Note**: The dataset combines information from OpenAlex (primary), Web of Science, and Scopus, with preference given to the most complete and highest quality data available from each source for individual fields.


```{r setup, echo=F, eval =T, warning = F}
rm(list = ls())
source('core_utilities.R')
using('httr','stringr','dplyr','tidyr','tidyRSS','jsonlite','lubridate','ggplot2','readxl','readr','purrr','knitr','tibble', 'arrow','jsonlite')
using('VennDiagram','kableExtra','RColorBrewer','gridExtra','scales')

paper.details.oa = read_parquet('Data/publication_combined_2000_2024.parquet')

# paper.details.oa = filter(paper.details.oa,!is_retracted) %>% select(-is_retracted)

paper.details.oa = paper.details.oa %>% 
rename(`document type` = type) %>%
filter(!grepl('retract', `document type`)) %>%  
# filter(`document type` %in% c('article','book','book-chapter','dataset','letter','reference-entry','report','review', 'editorial')) %>% 
ungroup() %>%
  mutate(doi = tolower(doi))

paper.details.ws = read_parquet('Data/publication_details_WoS-Scopus.parquet')

#Retain articles - remove letters, notes, errata
#Document types are mostly derived from Scopus. Look at https://www.ilovephd.com/list-of-document-types-covered-in-scopus/ - for details of what they refer to
paper.details.ws = paper.details.ws %>% 
# filter((grepl('(Article|Review|Book)',`document type`) | `document type` %in% c('Conference paper','Data paper','Proceedings Paper', 'Review', 'Short survey','Editorial')) & !grepl('Retract', `document type`)) %>%
filter(!grepl('Retract', `document type`)) %>%  
select(-pubNum)

# Add source information and match the two datasets by doi
dois = paper.details.ws %>% select(doi,datasource) %>%
mutate(Scopus = datasource %in% c('Both','Scopus'),
WoS = datasource %in% c('Both','WoS'), doi = tolower(doi)) %>%
full_join(paper.details.oa %>% select(doi) %>% mutate(openAlex = TRUE), by = join_by(doi)) %>% replace_na(list(Scopus = FALSE, WoS = FALSE, openAlex = FALSE)) %>% select(-datasource)

missing_oa = paper.details.ws %>% filter(doi %in% dois$doi[dois$openAlex == F])
# library(openalexR)
# addn.data = get_openalex_data(dois = missing_oa$doi)

# tot.papers = nrow(paper.details)
# 
# #report the data that we have
# printo('We have ',tot.papers,' publications pulled from Web of Science and Scopus in our analysis.')
# 
# printo('The data sources of these publications are as follows - \n',round(sum(paper.details$datasource == 'Both')/tot.papers*100),"% available in both databases,\n",round(sum(paper.details$datasource == 'Scopus')/tot.papers*100),"% available only from Scopus,\n",round(sum(paper.details$datasource == 'WoS')/tot.papers*100),"% available only from Web of Science.\n")
# 
# 

```


# Database Coverage Analysis

```{r coverage-analysis, fig.width=8, fig.height=4, warning=FALSE, message=FALSE, echo = F}
# library(dplyr)
# library(ggplot2)
# library(VennDiagram)
# library(RColorBrewer)
# library(gridExtra)
# library(scales)
# library(tidyr)

# Calculate coverage statistics
coverage_stats <- dois %>%
  summarise(
    total_dois = n(),
    scopus_coverage = sum(Scopus, na.rm = TRUE),
    wos_coverage = sum(WoS, na.rm = TRUE),
    openalex_coverage = sum(openAlex, na.rm = TRUE),
    scopus_pct = round(100 * scopus_coverage / total_dois, 1),
    wos_pct = round(100 * wos_coverage / total_dois, 1),
    openalex_pct = round(100 * openalex_coverage / total_dois, 1)
  )

# Create overlap analysis
overlap_analysis <- dois %>%
  mutate(
    coverage_pattern = case_when(
      Scopus & WoS & openAlex ~ "All three databases",
      Scopus & WoS & !openAlex ~ "Scopus + WoS only",
      Scopus & !WoS & openAlex ~ "Scopus + OpenAlex only",
      !Scopus & WoS & openAlex ~ "WoS + OpenAlex only",
      Scopus & !WoS & !openAlex ~ "Scopus only",
      !Scopus & WoS & !openAlex ~ "WoS only",
      !Scopus & !WoS & openAlex ~ "OpenAlex only",
      TRUE ~ "None"
    )
  ) %>%
  count(coverage_pattern) %>%
  mutate(
    percentage = round(100 * n / sum(n), 1),
    coverage_pattern = factor(coverage_pattern, levels = c(
      "All three databases", "Scopus + WoS only", "Scopus + OpenAlex only", 
      "WoS + OpenAlex only", "Scopus only", "WoS only", "OpenAlex only", "None"
    ))
  )

# 1. Overall coverage bar chart
p1 <- coverage_stats %>%
  select(ends_with("_coverage")) %>%
  pivot_longer(everything(), names_to = "database", values_to = "count") %>%
  mutate(
    database = case_when(
      database == "scopus_coverage" ~ "Scopus",
      database == "wos_coverage" ~ "Web of Science",
      database == "openalex_coverage" ~ "OpenAlex"
    ),
    percentage = round(100 * count / coverage_stats$total_dois, 1),
    database = factor(database, levels = c("OpenAlex", "Scopus", "Web of Science"))
  ) %>%
  ggplot(aes(x = database, y = count, fill = database)) +
  geom_col(width = 0.6, alpha = 0.9) +
  geom_text(aes(label = paste0(comma(count), "\n(", percentage, "%)")), 
            vjust = -0.5, size = 4, fontface = "bold", color = "black") +
  scale_fill_manual(values = c("Scopus" = "#E31A1C", "Web of Science" = "#1F78B4", "OpenAlex" = "#33A02C")) +
  scale_y_continuous(labels = comma_format(), expand = expansion(mult = c(0, 0.1))) +
  labs(
    title = "Database Coverage Comparison",
    subtitle = paste("Total DOIs analyzed:", comma(coverage_stats$total_dois)),
    x = "Database",
    y = "Number of DOIs Covered"
  ) +
  theme_minimal() +
  theme(
    legend.position = "none",
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(size = 13, hjust = 0.5),
    axis.text = element_text(size = 12),
    axis.title = element_text(size = 13),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  )

# 2. Overlap patterns with better colors
color_palette <- c(
  "All three databases" = "#2E8B57",
  "Scopus + WoS only" = "#FF6347", 
  "Scopus + OpenAlex only" = "#4169E1",
  "WoS + OpenAlex only" = "#FF8C00",
  "Scopus only" = "#E31A1C",
  "WoS only" = "#1F78B4",
  "OpenAlex only" = "#33A02C"
)

p2 <- overlap_analysis %>%
  filter(coverage_pattern != "None") %>%
  ggplot(aes(x = reorder(coverage_pattern, n), y = n, fill = coverage_pattern)) +
  geom_col(width = 0.7, alpha = 0.9) +
  geom_text(aes(label = paste0(comma(n), "\n(", percentage, "%)")), 
            hjust = -0.1, size = 3.8, fontface = "bold") +
  scale_fill_manual(values = color_palette) +
  scale_y_continuous(labels = comma_format(), expand = expansion(mult = c(0, 0.12))) +
  coord_flip() +
  labs(
    title = "Database Overlap Patterns",
    subtitle = "Distribution of DOIs across different database combinations",
    x = "Coverage Pattern",
    y = "Number of DOIs"
  ) +
  theme_minimal() +
  theme(
    legend.position = "none",
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(size = 13, hjust = 0.5),
    axis.text = element_text(size = 11),
    axis.title = element_text(size = 13),
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank()
  )

# 3. Create summary table
coverage_table <- overlap_analysis %>%
  arrange(desc(n)) %>%
  mutate(
    Pattern = coverage_pattern,
    Count = comma(n),
    Percentage = paste0(percentage, "%")
  ) %>%
  select(Pattern, Count, Percentage)

# Combine the two main plots
combined_plots <- grid.arrange(p1, p2, ncol = 2, widths = c(1, 1.2))

# Print the combined plots
print(combined_plots)

ggsave(combined_plots, file = 'plots/Database coverage statistics.png', width = 7, height = 3.5, units = 'in', scale = 2)
```

### Coverage Summary Table

```{r coverage-table, results='asis', echo = F}


kable(coverage_table, 
      caption = "Database Coverage Pattern Distribution",
      align = c("l", "r", "r")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE,
                position = "center") %>%
  row_spec(1, bold = TRUE, background = "#f0f0f0")
```

### Key Findings

```{r coverage-summary, results='asis', echo = F}
# Generate summary statistics
cat("**Database Coverage Summary:**\n\n")
cat("- **Scopus**: ", comma(coverage_stats$scopus_coverage), " DOIs (", coverage_stats$scopus_pct, "%)\n")
cat("- **Web of Science**: ", comma(coverage_stats$wos_coverage), " DOIs (", coverage_stats$wos_pct, "%)\n")
cat("- **OpenAlex**: ", comma(coverage_stats$openalex_coverage), " DOIs (", coverage_stats$openalex_pct, "%)\n\n")

# Coverage overlap insights
complete_coverage <- overlap_analysis %>% filter(coverage_pattern == "All three") %>% pull(n)
cat("**Coverage Overlap:**\n\n")
cat("- **All three databases**: ", comma(complete_coverage), " DOIs (", 
    round(100 * complete_coverage / coverage_stats$total_dois, 1), "%)\n")

# Unique coverage
unique_coverage <- overlap_analysis %>% 
  filter(coverage_pattern %in% c("Scopus only", "WoS only", "OpenAlex only")) %>%
  summarise(total = sum(n)) %>% pull(total)
cat("- **Unique to one database**: ", comma(unique_coverage), " DOIs (", 
    round(100 * unique_coverage / coverage_stats$total_dois, 1), "%)\n\n")

# Database-specific insights
cat("**Database-Specific Insights:**\n\n")
if (coverage_stats$openalex_pct > coverage_stats$scopus_pct & coverage_stats$openalex_pct > coverage_stats$wos_pct) {
  cat("- OpenAlex shows the highest coverage, reflecting its open-access focus and broader indexing approach\n")
} else if (coverage_stats$scopus_pct > coverage_stats$wos_pct) {
  cat("- Scopus demonstrates higher coverage than Web of Science in this dataset\n")
} else {
  cat("- Web of Science shows competitive coverage compared to other databases\n")
}

# missing_from_all <- coverage_stats$total_dois - max(coverage_stats$scopus_coverage, coverage_stats$wos_coverage, coverage_stats$openalex_coverage)
# if (missing_from_all > 0) {
#   cat("- ", comma(missing_from_all), " DOIs are missing from at least one major database, highlighting the value of multi-database searches\n")
# }

printo('Directly doing a search on openAlex for co-authored Indo Swiss publications results in only 19130 results. There are some limitations in their search tool that leads to lower coverage. After looking through the additional data provided by Web of Science and Scopus, we then searched for those papers on Open Alex and were able to raise the total OpenAlex data coverage to ',nrow(paper.details.oa),' entries.')

```

```{r coverage-analysis-old, include=F, eval=F, fig.width=12, fig.height=10, warning=FALSE}
library(dplyr)
library(ggplot2)
library(VennDiagram)
library(RColorBrewer)
library(gridExtra)
library(scales)
library(ggalluvial)

# Calculate coverage statistics
coverage_stats <- dois %>%
  summarise(
    total_dois = n(),
    scopus_coverage = sum(Scopus, na.rm = TRUE),
    wos_coverage = sum(WoS, na.rm = TRUE),
    openalex_coverage = sum(openAlex, na.rm = TRUE),
    scopus_pct = round(100 * scopus_coverage / total_dois, 1),
    wos_pct = round(100 * wos_coverage / total_dois, 1),
    openalex_pct = round(100 * openalex_coverage / total_dois, 1)
  )

# Create overlap analysis
overlap_analysis <- dois %>%
  mutate(
    coverage_pattern = case_when(
      Scopus & WoS & openAlex ~ "All three",
      Scopus & WoS & !openAlex ~ "Scopus + WoS only",
      Scopus & !WoS & openAlex ~ "Scopus + OpenAlex only",
      !Scopus & WoS & openAlex ~ "WoS + OpenAlex only",
      Scopus & !WoS & !openAlex ~ "Scopus only",
      !Scopus & WoS & !openAlex ~ "WoS only",
      !Scopus & !WoS & openAlex ~ "OpenAlex only",
      TRUE ~ "None"
    )
  ) %>%
  count(coverage_pattern) %>%
  mutate(
    percentage = round(100 * n / sum(n), 1),
    coverage_pattern = factor(coverage_pattern, levels = c(
      "All three", "Scopus + WoS only", "Scopus + OpenAlex only", 
      "WoS + OpenAlex only", "Scopus only", "WoS only", "OpenAlex only", "None"
    ))
  )

# 1. Overall coverage bar chart
p1 <- coverage_stats %>%
  select(ends_with("_coverage")) %>%
  pivot_longer(everything(), names_to = "database", values_to = "count") %>%
  mutate(
    database = case_when(
      database == "scopus_coverage" ~ "Scopus",
      database == "wos_coverage" ~ "Web of Science",
      database == "openalex_coverage" ~ "OpenAlex"
    ),
    percentage = round(100 * count / coverage_stats$total_dois, 1)
  ) %>%
  ggplot(aes(x = reorder(database, count), y = count, fill = database)) +
  geom_col(width = 0.7, alpha = 0.8) +
  geom_text(aes(label = paste0(comma(count), "\n(", percentage, "%)")), 
            hjust = -0.1, size = 3.5, fontface = "bold") +
  scale_fill_manual(values = c("Scopus" = "#E31A1C", "Web of Science" = "#1F78B4", "OpenAlex" = "#33A02C")) +
  scale_y_continuous(labels = comma_format(), expand = expansion(mult = c(0, 0.15))) +
  coord_flip() +
  labs(
    title = "Database Coverage Comparison",
    subtitle = paste("Total DOIs analyzed:", comma(coverage_stats$total_dois)),
    x = "Database",
    y = "Number of DOIs Covered"
  ) +
  theme_minimal() +
  theme(
    legend.position = "none",
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.text = element_text(size = 11),
    axis.title = element_text(size = 12)
  )

# 2. Overlap patterns
p2 <- overlap_analysis %>%
  filter(coverage_pattern != "None") %>%
  ggplot(aes(x = reorder(coverage_pattern, n), y = n, fill = coverage_pattern)) +
  geom_col(width = 0.7, alpha = 0.8) +
  geom_text(aes(label = paste0(comma(n), "\n(", percentage, "%)")), 
            hjust = -0.1, size = 3.5, fontface = "bold") +
  scale_fill_brewer(type = "qual", palette = "Set2") +
  scale_y_continuous(labels = comma_format(), expand = expansion(mult = c(0, 0.15))) +
  coord_flip() +
  labs(
    title = "Database Overlap Patterns",
    subtitle = "Distribution of DOIs across different database combinations",
    x = "Coverage Pattern",
    y = "Number of DOIs"
  ) +
  theme_minimal() +
  theme(
    legend.position = "none",
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.text = element_text(size = 11),
    axis.title = element_text(size = 12)
  )

# 3. Venn diagram data preparation
venn_data <- dois %>%
  summarise(
    scopus_only = sum(Scopus & !WoS & !openAlex),
    wos_only = sum(!Scopus & WoS & !openAlex),
    openalex_only = sum(!Scopus & !WoS & openAlex),
    scopus_wos = sum(Scopus & WoS & !openAlex),
    scopus_openalex = sum(Scopus & !WoS & openAlex),
    wos_openalex = sum(!Scopus & WoS & openAlex),
    all_three = sum(Scopus & WoS & openAlex)
  )

# Create Venn diagram
venn_plot <- draw.triple.venn(
  area1 = coverage_stats$scopus_coverage,
  area2 = coverage_stats$wos_coverage,
  area3 = coverage_stats$openalex_coverage,
  n12 = venn_data$scopus_wos + venn_data$all_three,
  n23 = venn_data$wos_openalex + venn_data$all_three,
  n13 = venn_data$scopus_openalex + venn_data$all_three,
  n123 = venn_data$all_three,
  category = c("Scopus", "Web of Science", "OpenAlex"),
  fill = c("#E31A1C", "#1F78B4", "#33A02C"),
  alpha = 0.6,
  cex = 1.5,
  cat.cex = 1.2,
  cat.fontface = "bold",
  margin = 0.1
)


# Combine plots
grid.arrange(p1, p2, ncol = 2)
grid.draw(venn_plot)

```

```{r Extracting topic information, echo = F, warning=F}
 # Function to parse topics JSON and extract primary topic
parse_primary_topic <- function(topics_json) {
  if (is.na(topics_json) || topics_json == "" || is.null(topics_json)) {
    return(list(
      primary_topic_id = NA_character_,
      primary_topic_name = NA_character_,
      primary_topic_score = NA_real_,
      primary_subfield_id = NA_character_,
      primary_subfield_name = NA_character_,
      primary_field_id = NA_character_,
      primary_field_name = NA_character_,
      primary_domain_id = NA_character_,
      primary_domain_name = NA_character_
    ))
  }
  
  tryCatch({
    # Parse JSON
    topics_list <- fromJSON(topics_json)
    
    # Filter for the first topic (i == 1) and get all hierarchy levels
    primary_entries <- topics_list[topics_list$i == 1, ]
    
    if (nrow(primary_entries) == 0) {
      return(list(
        primary_topic_id = NA_character_,
        primary_topic_name = NA_character_,
        primary_topic_score = NA_real_,
        primary_subfield_id = NA_character_,
        primary_subfield_name = NA_character_,
        primary_field_id = NA_character_,
        primary_field_name = NA_character_,
        primary_domain_id = NA_character_,
        primary_domain_name = NA_character_
      ))
    }
    
    # Extract topic information
    topic_info <- primary_entries[primary_entries$type == "topic", ]
    subfield_info <- primary_entries[primary_entries$type == "subfield", ]
    field_info <- primary_entries[primary_entries$type == "field", ]
    domain_info <- primary_entries[primary_entries$type == "domain", ]
    
    return(list(
      primary_topic_id = if(nrow(topic_info) > 0) topic_info$id[1] else NA_character_,
      primary_topic_name = if(nrow(topic_info) > 0) topic_info$display_name[1] else NA_character_,
      primary_topic_score = if(nrow(topic_info) > 0) topic_info$score[1] else NA_real_,
      primary_subfield_id = if(nrow(subfield_info) > 0) subfield_info$id[1] else NA_character_,
      primary_subfield_name = if(nrow(subfield_info) > 0) subfield_info$display_name[1] else NA_character_,
      primary_field_id = if(nrow(field_info) > 0) field_info$id[1] else NA_character_,
      primary_field_name = if(nrow(field_info) > 0) field_info$display_name[1] else NA_character_,
      primary_domain_id = if(nrow(domain_info) > 0) domain_info$id[1] else NA_character_,
      primary_domain_name = if(nrow(domain_info) > 0) domain_info$display_name[1] else NA_character_
    ))
  }, error = function(e) {
    warning(paste("Error parsing topics JSON:", e$message))
    return(list(
      primary_topic_id = NA_character_,
      primary_topic_name = NA_character_,
      primary_topic_score = NA_real_,
      primary_subfield_id = NA_character_,
      primary_subfield_name = NA_character_,
      primary_field_id = NA_character_,
      primary_field_name = NA_character_,
      primary_domain_id = NA_character_,
      primary_domain_name = NA_character_
    ))
  })
}

# Apply to your dataframe
print("Parsing topics data...")
topics_parsed <- map_dfr(paper.details.oa$topics, parse_primary_topic)

# Add the parsed topics to your dataframe
paper.details.oa <- paper.details.oa %>%
  bind_cols(topics_parsed)

print("Topics parsing complete!")

# Show summary of parsed data
cat("Summary of parsed topics:\n")
cat("- Total publications:", nrow(paper.details.oa), "\n")
cat("- Publications with primary topic:", sum(!is.na(paper.details.oa$primary_topic_id)), "\n")
cat("- Publications without topic data:", sum(is.na(paper.details.oa$primary_topic_id)), "\n")

# Show top 10 most common primary topics
if (sum(!is.na(paper.details.oa$primary_topic_name)) > 0) {
  cat("\nTop 10 most common primary subfields:\n")
  top_topics <- paper.details.oa %>%
    filter(!is.na(primary_subfield_name)) %>%
    count(primary_subfield_name, sort = TRUE) %>%
    head(10)
  
  for(i in 1:nrow(top_topics)) {
    cat(paste0(i, ". ", top_topics$primary_subfield_name[i], " (", top_topics$n[i], " papers)\n"))
  }
  
  cat("\nTop 10 most common primary Fields:\n")
  top_topics <- paper.details.oa %>%
    filter(!is.na(primary_field_name)) %>%
    count(primary_field_name, sort = TRUE) %>%
    head(10)
  
  for(i in 1:nrow(top_topics)) {
    cat(paste0(i, ". ", top_topics$primary_field_name[i], " (", top_topics$n[i], " papers)\n"))
  }
}

# Optional: If you also want to keep all topics in a proper list-column format
parse_all_topics <- function(topics_json) {
  if (is.na(topics_json) || topics_json == "" || is.null(topics_json)) {
    return(list(tibble()))
  }
  
  tryCatch({
    topics_list <- fromJSON(topics_json)
    return(list(as_tibble(topics_list)))
  }, error = function(e) {
    return(list(tibble()))
  })
}

# Uncomment the following lines if you want to keep all topics as well
# print("Creating list-column for all topics...")
# paper.details.oa$all_topics <- map(paper.details.oa$topics, parse_all_topics)

# Clean up (remove the original JSON column if desired)
paper.details.oa <- paper.details.oa %>% select(-topics)

print("Dataset updated with primary topic information!")
```

```{r Data Enhancement while merging, echo = F}
# Function to get longer text between two columns
get_longer_text <- function(col1, col2) {
  result <- character(length(col1))
  
  for(i in seq_along(col1)) {
    val1 <- if(is.na(col1[i]) || col1[i] == "") "" else col1[i]
    val2 <- if(is.na(col2[i]) || col2[i] == "") "" else col2[i]
    
    if(nchar(val1) >= nchar(val2)) {
      result[i] <- if(val1 == "") NA_character_ else val1
    } else {
      result[i] <- if(val2 == "") NA_character_ else val2
    }
  }
  return(result)
}

# Function to count non-NA values
count_non_na <- function(x) sum(!is.na(x) & x != "")

cat("=== COMPREHENSIVE DATA ENHANCEMENT ===\n\n")

# Step 1: Prepare missing papers for addition
cat("Step 1: Preparing missing papers for addition...\n")

missing_enhanced <- missing_oa %>%
  mutate(
    # Basic OpenAlex structure
    work_id = NA_character_,
    title = `article title`,
    display_name = `article title`,
    
    # Abstract - prefer Scopus over WoS
    abstract = case_when(
      !is.na(abstract.s) & abstract.s != "" ~ abstract.s,
      !is.na(abstract.w) & abstract.w != "" ~ abstract.w,
      TRUE ~ NA_character_
    ),
    
    # Citation count - maximum across all sources
    cited_by_count = pmax(
      ifelse(is.na(times_cited.s), 0, times_cited.s),
      ifelse(is.na(times_cited.w), 0, times_cited.w),
      na.rm = TRUE
    ),
    
    # Document type - convert to lowercase
    `document type` = tolower(`document type`),
    
    # Publication info
    publication_date = as.Date(paste0(year, "-01-01")),
    publication_year = as.integer(year),
    
    # Source info
    source_display_name = `source title`,
    
    # Funding details - choose longer text
    funding_details = get_longer_text(`funding details.s`, `funding details.w`),
    funding_text = get_longer_text(`funding text.s`, `funding text.w`),
    
    # Keywords - keep all
    author_keywords = `author keywords`,
    index_keywords_scopus = index_keywords_scopus,
    keywords_plus_wos = keywords_plus_wos,
    
    # Add other columns to match OpenAlex structure
    ids = NA_character_,
    is_oa = NA,
    source_id = NA_character_,
    issn_l = NA_character_,
    host_organization = NA_character_,
    host_organization_name = NA_character_,
    landing_page_url = NA_character_,
    pdf_url = NA_character_,
    license = NA_character_,
    version = NA_character_,
    keywords = NA_character_,
    is_retracted = FALSE,
    grants = NA_character_,
    primary_topic_id = NA_character_,
    primary_topic_name = NA_character_,
    primary_topic_score = NA_real_,
    primary_subfield_id = NA_character_,
    primary_subfield_name = NA_character_,
    primary_field_id = NA_character_,
    primary_field_name = NA_character_,
    primary_domain_id = NA_character_,
    primary_domain_name = NA_character_
  ) %>%
  select(all_of(names(paper.details.oa)), funding_details, funding_text, 
         author_keywords, index_keywords_scopus, keywords_plus_wos)

cat("✓ Prepared", nrow(missing_enhanced), "missing papers for addition\n")

# Step 2: Enhance existing OpenAlex data
cat("\nStep 2: Enhancing existing OpenAlex data with WoS/Scopus information...\n")

# Create a lookup from the full paper.details.ws
ws_lookup <- paper.details.ws %>%
  filter(doi %in% paper.details.oa$doi) %>%
  mutate(
    # Enhanced abstract - prefer Scopus
    enhanced_abstract = case_when(
      !is.na(abstract.s) & abstract.s != "" ~ abstract.s,
      !is.na(abstract.w) & abstract.w != "" ~ abstract.w,
      TRUE ~ NA_character_
    ),
    
    # Enhanced citation count
    enhanced_citations = pmax(
      ifelse(is.na(times_cited.s), 0, times_cited.s),
      ifelse(is.na(times_cited.w), 0, times_cited.w),
      na.rm = TRUE
    ),
    
    # Funding details
    funding_details = get_longer_text(`funding details.s`, `funding details.w`),
    funding_text = get_longer_text(`funding text.s`, `funding text.w`),
    
    # Keywords
    author_keywords = `author keywords`,
    index_keywords_scopus = index_keywords_scopus,
    keywords_plus_wos = keywords_plus_wos
  ) %>%
  select(doi, enhanced_abstract, enhanced_citations, funding_details, funding_text,
         author_keywords, index_keywords_scopus, keywords_plus_wos)

# Merge with OpenAlex data
paper.details.oa.enhanced <- paper.details.oa %>%
  left_join(ws_lookup, by = "doi") %>%
  mutate(
    # Update abstract if missing in OpenAlex
    abstract = case_when(
      is.na(abstract) & !is.na(enhanced_abstract) ~ enhanced_abstract,
      TRUE ~ abstract
    ),
    
    # Update citation count with maximum
    cited_by_count = pmax(
      ifelse(is.na(cited_by_count), 0, cited_by_count),
      ifelse(is.na(enhanced_citations), 0, enhanced_citations),
      na.rm = TRUE
    ),
    
    # Convert document type to lowercase
    `document type` = tolower(`document type`)
  ) %>%
  select(-enhanced_abstract, -enhanced_citations)

cat("✓ Enhanced", nrow(paper.details.oa.enhanced), "existing OpenAlex papers\n")

# Step 3: Combine datasets
cat("\nStep 3: Combining datasets...\n")

# Ensure both datasets have the same columns
common_cols <- intersect(names(paper.details.oa.enhanced), names(missing_enhanced))
final_dataset <- bind_rows(
  paper.details.oa.enhanced[common_cols],
  missing_enhanced[common_cols]
)

cat("✓ Combined dataset has", nrow(final_dataset), "total papers\n")

# Step 4: Generate comprehensive report
cat("\n=== ENHANCEMENT REPORT ===\n")

# Abstract enhancement
original_abstracts <- sum(!is.na(paper.details.oa$abstract) & paper.details.oa$abstract != "")
enhanced_abstracts <- sum(!is.na(final_dataset$abstract) & final_dataset$abstract != "")
cat("Abstract Enhancement:\n")
cat("- Original abstracts with just OpenAlex:", original_abstracts, "\n")
cat("- Enhanced abstracts:", enhanced_abstracts, "\n")
cat("- Abstracts added:", enhanced_abstracts - original_abstracts, "\n")

# Citation enhancement
original_citations <- sum(!is.na(paper.details.oa$cited_by_count) & paper.details.oa$cited_by_count > 0)
enhanced_citations <- sum(!is.na(final_dataset$cited_by_count) & final_dataset$cited_by_count > 0)
cat("\nCitation Enhancement:\n")
cat("- Original citations:", original_citations, "\n")
cat("- Enhanced citations:", enhanced_citations, "\n")
cat("- Citations added/updated:", enhanced_citations - original_citations, "\n")

# Funding analysis
cat("\nFunding Details Analysis:\n")
funding_details_count <- count_non_na(final_dataset$funding_details)
funding_text_count <- count_non_na(final_dataset$funding_text)
original_grants <- count_non_na(paper.details.oa$grants)

cat("- Original OpenAlex grants:", original_grants, "\n")
cat("- Enhanced funding details:", funding_details_count, "\n")
cat("- Enhanced funding text:", funding_text_count, "\n")
cat("- Total funding improvement:", funding_details_count - original_grants, "\n")

# Funding source analysis (for papers present in both)
if(nrow(ws_lookup) > 0) {
  scopus_funding_better <- sum(
    nchar(ifelse(is.na(paper.details.ws$`funding details.s`), "", paper.details.ws$`funding details.s`)) >
    nchar(ifelse(is.na(paper.details.ws$`funding details.w`), "", paper.details.ws$`funding details.w`)),
    na.rm = TRUE
  )
  
  wos_funding_better <- sum(
    nchar(ifelse(is.na(paper.details.ws$`funding details.w`), "", paper.details.ws$`funding details.w`)) >
    nchar(ifelse(is.na(paper.details.ws$`funding details.s`), "", paper.details.ws$`funding details.s`)),
    na.rm = TRUE
  )
  
  cat("- Scopus funding details are better than WoS:", scopus_funding_better, "times\n")
  cat("- WoS funding details are better than Scoups:", wos_funding_better, "times\n")
}

# Keywords enhancement
oa_kw_count <- count_non_na(paper.details.oa$keywords)
author_kw_count <- count_non_na(final_dataset$author_keywords)
scopus_kw_count <- count_non_na(final_dataset$index_keywords_scopus)
wos_kw_count <- count_non_na(final_dataset$keywords_plus_wos)

cat("\nKeywords Enhancement:\n")
cat("- Author keywords from OpenAlex:", oa_kw_count, "\n")
cat("- Author keywords from WoS and Scopus:", author_kw_count, "\n")
cat("- Scopus index keywords:", scopus_kw_count, "\n")
cat("- WoS keywords plus:", wos_kw_count, "\n")

printo('So keywords information is generally sufficient just from OpenAlex')

# Document type conversion
cat("\nThese are the types and counts of documents found in this compilation:\n")
doc_types <- table(final_dataset$`document type`)
for(i in seq_along(doc_types)) {
  cat("-", names(doc_types)[i], ":", doc_types[i], "\n")
}

cat("\n=== FINAL DATASET SUMMARY ===\n")
cat("Total papers:", nrow(final_dataset), "\n")
cat("Papers with abstracts:", sum(!is.na(final_dataset$abstract) & final_dataset$abstract != ""), "\n")
cat("Papers with citations:", sum(!is.na(final_dataset$cited_by_count) & final_dataset$cited_by_count > 0), "\n")
cat("Papers with funding info:", sum(!is.na(final_dataset$funding_details) & final_dataset$funding_details != ""), "\n")
cat("Papers with OpenAlex topics:", sum(!is.na(final_dataset$primary_topic_name)), "\n")

# Save the enhanced dataset
paper.details.oa.final <- final_dataset
cat("\n✓ Enhanced dataset saved as 'paper.details.oa.final'\n")

# Optional: Show sample of enhancements
# cat("\n=== SAMPLE ENHANCEMENTS ===\n")
# sample_enhanced <- final_dataset %>%
#   filter(!is.na(funding_details) & funding_details != "") %>%
#   slice_head(n = 3) %>%
#   select(title, funding_details) %>%
#   mutate(
#     title = str_trunc(title, 50),
#     funding_details = str_trunc(funding_details, 100)
#   )
# 
# if(nrow(sample_enhanced) > 0) {
#   cat("Sample papers with funding details:\n")
#   for(i in 1:nrow(sample_enhanced)) {
#     cat(i, ".", sample_enhanced$title[i], "\n")
#     cat("   Funding:", sample_enhanced$funding_details[i], "\n\n")
#   }
# }

# cat("Enhancement complete! 🎉\n")


# write_parquet(paper.details.oa.final, 'Data/publications_compiled_2000-2024.parquet')

```


```{r Add in author and institution information, echo = F, eval = F}

authors = read_parquet('Data/authorships_combined_2000_2024.parquet')
# Two-step processing: 5.4M row flat dataset -> 24K aggregated dataset
# Properly handles multiple affiliations per author and extracts countries

library(data.table)
library(jsonlite)

# Convert to data.table for speed
setDT(authors)

print("Starting Step 1: Processing 5.4M rows to extract institutions and countries...")
start_time1 <- Sys.time()

# Function to process JSON affiliations and extract institutions with countries
process_affiliations <- function(json_str) {
  if (is.na(json_str) || json_str == "" || json_str == "[]") {
    return(list(
      institutions_with_country = NA_character_,
      countries = NA_character_
    ))
  }
  
  tryCatch({
    parsed <- fromJSON(json_str)
    
    if (length(parsed) == 0) {
      return(list(
        institutions_with_country = NA_character_,
        countries = NA_character_
      ))
    }
    
    # Handle case where parsed is a data frame (multiple affiliations)
    if (is.data.frame(parsed)) {
      institutions <- character(0)
      countries <- character(0)
      
      for (i in 1:nrow(parsed)) {
        if (!is.na(parsed$display_name[i]) && parsed$display_name[i] != "") {
          country_code <- if (!is.na(parsed$country_code[i])) parsed$country_code[i] else "XX"
          institutions <- c(institutions, paste0(parsed$display_name[i], ", ", country_code))
          countries <- c(countries, country_code)
        }
      }
      
      if (length(institutions) > 0) {
        return(list(
          institutions_with_country = paste(institutions, collapse = "; "),
          countries = paste(unique(countries[countries != "XX"]), collapse = ", ")
        ))
      }
    }
    
    # Handle case where parsed is a single record (one affiliation)
    else if (is.list(parsed) && "display_name" %in% names(parsed)) {
      if (!is.na(parsed$display_name) && parsed$display_name != "") {
        country_code <- if (!is.na(parsed$country_code)) parsed$country_code else "XX"
        return(list(
          institutions_with_country = paste0(parsed$display_name, ", ", country_code),
          countries = if (country_code != "XX") country_code else ""
        ))
      }
    }
    
    return(list(
      institutions_with_country = NA_character_,
      countries = NA_character_
    ))
    
  }, error = function(e) {
    return(list(
      institutions_with_country = NA_character_,
      countries = NA_character_
    ))
  })
}

# Process unique affiliations first to avoid redundant parsing
print("Processing unique JSON affiliations...")
unique_affiliations <- unique(authors$affiliations[!is.na(authors$affiliations)])
print(paste("Found", length(unique_affiliations), "unique affiliation JSONs to parse"))

# Create lookup table
affiliation_results <- rbindlist(lapply(unique_affiliations, function(aff) {
  result <- process_affiliations(aff)
  data.table(
    affiliations = aff,
    institutions_with_country = result$institutions_with_country,
    author_countries = result$countries
  )
}))

print("Joining parsed affiliations back to main dataset...")

# Join back to main authors table
authors_processed <- authors[affiliation_results, on = "affiliations", nomatch = 0]

# For rows that didn't match (NA affiliations), add them back with NA values
authors_na <- authors[is.na(affiliations)]
if (nrow(authors_na) > 0) {
  authors_na[, c("institutions_with_country", "author_countries") := list(NA_character_, NA_character_)]
  authors_processed <- rbind(authors_processed, authors_na, fill = TRUE)
}

# Clean up the processed dataset
authors_processed[institutions_with_country == "", institutions_with_country := NA_character_]
authors_processed[author_countries == "", author_countries := NA_character_]

# Add columns for number of institutions and countries per author
authors_processed[, n_institutions_author := {
  if (is.na(institutions_with_country)) {
    0L
  } else {
    length(strsplit(institutions_with_country, "; ")[[1]])
  }
}, by = 1:nrow(authors_processed)]

authors_processed[, n_countries_author := {
  if (is.na(author_countries)) {
    0L
  } else {
    length(unique(strsplit(author_countries, ", ")[[1]]))
  }
}, by = 1:nrow(authors_processed)]

end_time1 <- Sys.time()
print(paste("Step 1 completed in:", round(difftime(end_time1, start_time1, units = "secs"), 2), "seconds"))
print(paste("Processed dataset has", nrow(authors_processed), "rows"))

# Display sample results
print("\nSample of processed data:")
sample_rows <- authors_processed[!is.na(institutions_with_country)][1:3]
print(sample_rows[, .(work_id, display_name, institutions_with_country, author_countries)])

# Save the flat 5.4M row dataset as parquet
print("\nSaving flat processed dataset as parquet...")
library(arrow)
write_parquet(authors_processed, "authors_processed_flat.parquet")

print("\n--------------------------------------"))
print("Starting Step 2: Aggregating to 24K publication-level dataset...")
start_time2 <- Sys.time()

# Step 2: Aggregate to publication level
publication_summary <- authors_processed[, {
  # Get all non-NA authors
  valid_authors <- display_name[!is.na(display_name) & display_name != ""]
  
  # Get all non-NA institutions with countries and make them unique
  valid_institutions <- institutions_with_country[!is.na(institutions_with_country) & institutions_with_country != ""]
  # Split, flatten, and get unique institutions
  all_institutions <- unlist(strsplit(valid_institutions, "; "))
  unique_institutions <- unique(all_institutions[all_institutions != ""])
  
  # Get all countries mentioned by any author for this paper
  all_countries <- unlist(strsplit(author_countries[!is.na(author_countries) & author_countries != ""], ", "))
  unique_countries <- unique(all_countries[all_countries != ""])
  
  list(
    authors_combined = if(length(valid_authors) > 0) paste(valid_authors, collapse = "; ") else NA_character_,
    institutions_combined = if(length(unique_institutions) > 0) paste(unique_institutions, collapse = "; ") else NA_character_,
    countries_in_paper = if(length(unique_countries) > 0) paste(sort(unique_countries), collapse = ", ") else NA_character_,
    n_authors = .N,
    n_corresponding = sum(is_corresponding, na.rm = TRUE),
    n_authors_with_orcid = sum(!is.na(orcid)),
    n_authors_with_affiliations = sum(!is.na(institutions_with_country))
  )
}, by = work_id]

end_time2 <- Sys.time()
print(paste("Step 2 completed in:", round(difftime(end_time2, start_time2, units = "secs"), 2), "seconds"))

# Display results
print(paste("\nFinal dataset has", nrow(publication_summary), "publications"))
print("\nSample of aggregated results:")
sample_pubs <- publication_summary[!is.na(institutions_combined)][1:2]
print(sample_pubs)

publication_summary = publication_summary %>% mutate(work_id = str_remove_all(work_id,'https://openalex\\.org/'))

# Show a specific example to verify the processing
print("\nDetailed example of one publication:")
example_work <- publication_summary$work_id[1]
print(paste("Work ID:", example_work))
print("Authors for this work:")
example_authors <- authors_processed[work_id == example_work]
print(example_authors[, .(display_name, institutions_with_country, author_countries)])
print("Aggregated result:")
print(publication_summary[work_id == example_work])

# Save the aggregated 24K dataset as parquet
print("\nSaving aggregated publication dataset as parquet...")
write_parquet(publication_summary, "publications_with_institutions_countries.parquet")

paper.details.2 = paper.details.oa.final %>% left_join(publication_summary %>% select(work_id, authors = authors_combined, institutions = institutions_combined, countries = countries_in_paper, nAuthors = n_authors), by = 'work_id')

paper.details.2 = paper.details.2 %>% left_join(missing_oa %>% select(doi, authors1 = `author full names`, institutions1 = `affiliations`,nAuthors1 = nAuthors), by = 'doi') %>% as.data.table()
paper.details.2[!is.na(authors1), authors := authors1][!is.na(authors1), institutions := institutions1][!is.na(authors1), nAuthors := nAuthors1]

paper.details.2 = as_tibble(paper.details.2) %>% select(-authors1,-institutions1,-nAuthors1)

write_parquet(paper.details.2, 'Data/publications_full_dataset_2000-2024.parquet')

# Create institutional relationship table for India and Switzerland
print("\nCreating institutional relationship table for IN and CH...")
start_time3 <- Sys.time()

# Extract all institutions from the processed data that are in India or Switzerland
institutions_expanded <- authors_processed[!is.na(institutions_with_country), {
  # Split the institutions string and create one row per institution
  inst_list <- strsplit(institutions_with_country, "; ")[[1]]
  if (length(inst_list) > 0) {
    data.table(institution_with_country = inst_list)
  } else {
    data.table(institution_with_country = character(0))
  }
}, by = .(work_id, display_name)]

# Extract country codes and filter for India and Switzerland
institutions_expanded[, country_code := sub(".*,\\s*([A-Z]{2})$", "\\1", institution_with_country)]
institutions_expanded[, institution_name := sub(",\\s*[A-Z]{2}$", "", institution_with_country)]

# Filter for only India (IN) and Switzerland (CH)
institutions_in_ch <- institutions_expanded[country_code %in% c("IN", "CH")]

# Create the institutional relationship table
institutional_relationships <- institutions_in_ch[, {
  list(
    work_ids = paste(sort(unique(work_id)), collapse = "; "),
    n_publications = length(unique(work_id)),
    n_authors = length(unique(display_name)),
    author_names = paste(sort(unique(display_name)), collapse = "; ")
  )
}, by = .(institution_name, country_code)]

# Sort by country and number of publications
institutional_relationships <- institutional_relationships[order(country_code, -n_publications)]

end_time3 <- Sys.time()
print(paste("Institutional relationship table created in:", round(difftime(end_time3, start_time3, units = "secs"), 2), "seconds"))

print(paste("Found", nrow(institutional_relationships), "unique institutions from IN and CH"))
print("Top institutions by publication count:")
print(head(institutional_relationships[, .(institution_name, country_code, n_publications, n_authors)], 10))

# Save institutional relationships as parquet
print("\nSaving institutional relationship table as parquet...")
write_parquet(institutional_relationships, "Data/institutional_relationships_IN_CH.parquet")
openxlsx::write.xlsx(institutional_relationships %>% select(institution_name, country_code, n_publications, n_authors), "Data/institutional_relationships_IN_CH.xlsx")

# Summary statistics
print("\n--------------------------------------"))
print("PROCESSING SUMMARY:")
print(paste("Original rows:", nrow(authors)))
print(paste("Processed flat rows:", nrow(authors_processed)))
print(paste("Final publications:", nrow(publication_summary)))
print(paste("Publications with institutions:", sum(!is.na(publication_summary$institutions_combined))))
print(paste("Publications with country data:", sum(!is.na(publication_summary$countries_in_paper))))

total_time <- difftime(end_time2, start_time1, units = "secs")
print(paste("Total processing time:", round(total_time, 2), "seconds"))

print("\nFiles created:")
print("1. authors_processed_flat.parquet (5.4M rows with parsed institutions)")
print("2. publications_with_institutions_countries.parquet (24K publications aggregated)")
print("3. institutional_relationships_IN_CH.parquet (unique IN/CH institutions with their publications)")

print("\nInstitutional relationship table columns:")
print("- institution_name: Clean institution name")
print("- country_code: IN or CH")
print("- work_ids: Semicolon-separated list of publication IDs")
print("- n_publications: Number of publications from this institution")
print("- n_authors: Number of unique authors from this institution")
print("- author_names: Semicolon-separated list of author names")

print("\nProcessing complete!")

```


```{r Processing authors data, echo = F, warning=F}
library(data.table)
library(stringr)

# Fast author summary creation using data.table
create_author_summary_fast <- function(authors_processed) {
  
  print("Starting fast author summary creation...")
  start_time <- Sys.time()
  
  # Convert to data.table if not already
  if (!is.data.table(authors_processed)) {
    setDT(authors_processed)
  }
  
  print("Step 1: Creating institution work counts...")
  step1_time <- Sys.time()
  
  # Step 1: Create institution-work mapping
  # Expand institutions for each author-work combination
  institutions_expanded <- authors_processed[
    !is.na(author_id) & !is.na(institutions_with_country),
    .(work_id, author_id, institutions = unlist(strsplit(institutions_with_country, "; "))),
    by = .(work_id, author_id)
  ][institutions != ""]
  
  # Count works per author-institution
  institution_counts <- institutions_expanded[, .(n_works = uniqueN(work_id)), by = .(author_id, institutions)]
  
  # Create nested structure for institutions
  institution_lists <- institution_counts[, .(
    institution_work_counts = list(.SD[order(-n_works)])
  ), by = author_id]
  
  print(paste("Step 1 completed in:", round(difftime(Sys.time(), step1_time, units = "secs"), 2), "seconds"))
  
  print("Step 2: Creating country work counts...")
  step2_time <- Sys.time()
  
  # Step 2: Create country-work mapping  
  # Expand countries for each author-work combination
  countries_expanded <- authors_processed[
    !is.na(author_id) & !is.na(author_countries),
    .(work_id, author_id, countries = unlist(strsplit(author_countries, ", "))),
    by = .(work_id, author_id)
  ][countries != ""]
  
  # Count works per author-country
  country_counts <- countries_expanded[, .(n_works = uniqueN(work_id)), by = .(author_id, countries)]
  
  # Create nested structure for countries
  country_lists <- country_counts[, .(
    country_work_counts = list(.SD[order(-n_works)])
  ), by = author_id]
  
  print(paste("Step 2 completed in:", round(difftime(Sys.time(), step2_time, units = "secs"), 2), "seconds"))
  
  print("Step 3: Determining collaboration status...")
  step3_time <- Sys.time()
  
  # Step 3: Determine collaboration status for each author
  # First, check for India-Switzerland collaboration per work (for Joint category)
  work_country_check <- authors_processed[
    !is.na(author_id) & !is.na(author_countries),
    .(
      has_IN = any(grepl("IN", author_countries)),
      has_CH = any(grepl("CH", author_countries))
    ),
    by = .(author_id, work_id)
  ]
  
  # Check if any work for each author has both IN and CH (Joint collaboration)
  india_swiss_joint <- work_country_check[, .(
    has_india_swiss_collab = any(has_IN & has_CH)
  ), by = author_id]
  
  # Check overall affiliation patterns for each author across all their works
  author_country_patterns <- countries_expanded[, .(
    has_ever_IN = any(countries == "IN"),
    has_ever_CH = any(countries == "CH")
  ), by = author_id]
  
  # Merge collaboration data to determine collab_status
  collaboration_data <- merge(india_swiss_joint, author_country_patterns, by = "author_id", all = TRUE)
  
  # Handle missing values (authors with no country data)
  collaboration_data[is.na(has_india_swiss_collab), has_india_swiss_collab := FALSE]
  collaboration_data[is.na(has_ever_IN), has_ever_IN := FALSE]
  collaboration_data[is.na(has_ever_CH), has_ever_CH := FALSE]
  
  # Create categorical collab_status variable
  collaboration_data[, collab_status := fcase(
    # Joint: has both IN and CH affiliations in same paper(s)
    has_india_swiss_collab == TRUE, "Joint",
    # Both: has had both IN and CH affiliations but never in same paper
    has_ever_IN == TRUE & has_ever_CH == TRUE & has_india_swiss_collab == FALSE, "Both",
    # IN: has had Indian affiliation but never Swiss
    has_ever_IN == TRUE & has_ever_CH == FALSE, "IN",
    # CH: has had Swiss affiliation but never Indian
    has_ever_IN == FALSE & has_ever_CH == TRUE, "CH",
    # None: neither Indian nor Swiss affiliations
    default = "None"
  )]
  
  print(paste("Step 3 completed in:", round(difftime(Sys.time(), step3_time, units = "secs"), 2), "seconds"))
  
  print("Step 4: Creating main author summary...")
  step4_time <- Sys.time()
  
  # Step 4: Main author summary with basic metrics
  authors_main <- authors_processed[!is.na(author_id), .(
    name = first(display_name, na_rm = TRUE),
    orcid = first(orcid, na_rm = TRUE),
    nWorks = uniqueN(work_id, na.rm = TRUE),
    total_institutions = {
      all_insts <- unlist(strsplit(institutions_with_country[!is.na(institutions_with_country)], "; "))
      length(unique(all_insts[all_insts != ""]))
    },
    total_countries = {
      all_countries <- unlist(strsplit(author_countries[!is.na(author_countries)], ", "))
      length(unique(all_countries[all_countries != ""]))
    },
    n_corresponding_works = sum(is_corresponding, na.rm = TRUE)
  ), by = author_id]
  
  print(paste("Step 4 completed in:", round(difftime(Sys.time(), step4_time, units = "secs"), 2), "seconds"))
  
  print("Step 5: Merging all components...")
  step5_time <- Sys.time()
  
  # Step 5: Merge all components
  # Start with main summary
  final_summary <- authors_main
  
  # Add institution lists
  final_summary <- merge(final_summary, institution_lists, by = "author_id", all.x = TRUE)
  
  # Add country lists  
  final_summary <- merge(final_summary, country_lists, by = "author_id", all.x = TRUE)
  
  # Add collaboration status (categorical variable)
  final_summary <- merge(final_summary, collaboration_data[, .(author_id, collab_status)], 
                         by = "author_id", all.x = TRUE)
  
  # Fill missing collaboration status with "None"
  final_summary[is.na(collab_status), collab_status := "None"]
  
  # Handle missing list columns
  final_summary[is.na(institution_work_counts), institution_work_counts := list(list(data.table(institutions = character(0), n_works = integer(0))))]
  final_summary[is.na(country_work_counts), country_work_counts := list(list(data.table(countries = character(0), n_works = integer(0))))]
  
  # Order by number of works
  setorder(final_summary, -nWorks)
  
  print(paste("Step 5 completed in:", round(difftime(Sys.time(), step5_time, units = "secs"), 2), "seconds"))
  
  # Print summary of collaboration status distribution
  print("Collaboration status distribution:")
  print(final_summary[, .N, by = collab_status][order(-N)])
  
  end_time <- Sys.time()
  print(paste("Total processing time:", round(difftime(end_time, start_time, units = "secs"), 2), "seconds"))
  
  return(final_summary)
}

# Run the fast function
print("Processing 5.4M records with optimized data.table approach...")
authors_summ <- create_author_summary_fast(authors_processed)

# Display summary statistics
print(paste("Created summary for", nrow(authors_summ), "unique authors"))
print(paste("Authors with India-Swiss collaboration:", sum(authors_summ$has_india_swiss_collab)))

# Show examples - optimized display
print("\nTop 3 authors by number of works:")
top_3 <- head(authors_summ, 3)

for(i in 1:3) {
  cat("\n--------------------------------------------\n")
  cat("Author:", top_3$name[i], "\n")
  cat("Total works:", top_3$nWorks[i], "\n")
  cat("India-Swiss collaboration:", top_3$has_india_swiss_collab[i], "\n")
  cat("Total institutions:", top_3$total_institutions[i], "\n")
  cat("Total countries:", top_3$total_countries[i], "\n")
  
  # Show top institutions
  inst_data <- top_3$institution_work_counts[[i]]
  if(nrow(inst_data) > 0) {
    cat("Top institutions:\n")
    print(head(inst_data, 3))
  }
  
  # Show countries
  country_data <- top_3$country_work_counts[[i]]
  if(nrow(country_data) > 0) {
    cat("Countries:\n")
    print(country_data)
  }
}

# Fast exploration function
explore_author_fast <- function(author_name_pattern, authors_summ) {
  matches <- authors_summ[grepl(author_name_pattern, name, ignore.case = TRUE)]
  
  if(nrow(matches) == 0) {
    cat("No authors found matching:", author_name_pattern, "\n")
    return(invisible(NULL))
  }
  
  cat("Found", nrow(matches), "matching authors:\n")
  for(i in 1:min(5, nrow(matches))) {  # Limit to first 5 matches
    cat("\n", matches$name[i], "- Works:", matches$nWorks[i], 
        "- India-Swiss collab:", matches$has_india_swiss_collab[i], "\n")
    
    # Show top institutions
    inst_data <- matches$institution_work_counts[[i]]
    if(nrow(inst_data) > 0) {
      top_insts <- head(inst_data, 2)
      cat("Top institutions:", paste(paste0(top_insts$institutions, " (", top_insts$n_works, ")"), collapse = "; "), "\n")
    }
    
    # Show countries
    country_data <- matches$country_work_counts[[i]]
    if(nrow(country_data) > 0) {
      cat("Countries:", paste(paste0(country_data$countries, " (", country_data$n_works, ")"), collapse = ", "), "\n")
    }
  }
}

# Summary statistics - fast computation
print("\n", paste(rep("=", 60), collapse = ""))
print("SUMMARY STATISTICS:")
print(paste("Total authors:", nrow(authors_summ)))
print(paste("Authors with >10 works:", sum(authors_summ$nWorks > 10)))
print(paste("Authors with >50 works:", sum(authors_summ$nWorks > 50)))
print(paste("Authors with ORCID:", sum(!is.na(authors_summ$orcid))))
print(paste("Authors with India-Swiss collaboration:", sum(authors_summ$has_india_swiss_collab)))

# Fast work distribution
work_breaks <- c(1, 2, 6, 11, 26, 51, Inf)
work_labels <- c("1 work", "2-5 works", "6-10 works", "11-25 works", "26-50 works", ">50 works")
authors_summ[, work_category := cut(nWorks, breaks = work_breaks, labels = work_labels, right = FALSE)]

work_distribution <- authors_summ[, .N, by = work_cfategory][order(work_category)]
work_distribution[, percentage := round(N / sum(N) * 100, 1)]

print("\nWork distribution among authors:")
print(work_distribution)

print("\nSaving author summary...")
# Save the results efficiently
library(arrow)
write_parquet(authors_summ, "Data/authors_summary_with_lists.parquet")

print("Author summary saved to: authors_summary_with_lists.parquet")
print("\nExample usage:")
print("explore_author_fast('Kumar', authors_summ)")
print("explore_author_fast('Singh', authors_summ)")

```

