---
title: "Comparison of OpenAlex, Web of Science and Scopus"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

This file contains the comparison of data we get from OpenAlex from searching for Indo-Swiss coauthored publications over the past 25 years, and the comparison to Scopus and Web of Science.
It has been superseded by a later version of the database. OpenAlex has all the entries found in Web of Science and Scopus, we just had to query for those individual DOIs. Since the OpenAlex data is better structured, we are then proceeding with using only OpenAlex data for the whole analysis going ahead.

```{r setup, echo=F, eval =T}
rm(list = ls())
source('core_utilities.R')
using('httr','stringr','dplyr','tidyr','tidyRSS','jsonlite','lubridate','ggplot2','readxl','readr','purrr','knitr','tibble')
using('countries')

library(arrow)

paper.details = read_feather('Data/openAlex_paper_details_flat.feather')

paper.details = filter(paper.details,!is_retracted) %>% select(-is_retracted)

paper.details.ws = readRDS(file = 'Data/publication_details.RData')

#Retain articles - remove letters
#Document types are mostly derived from Scopus. Look at https://www.ilovephd.com/list-of-document-types-covered-in-scopus/ - for details of what they refer to

paper.details = paper.details %>% filter(document_type %in% c('article','book','book-chapter','dataset','letter','reference-entry','report','review')) %>% ungroup()

printo("We are selecting only articles of the following types - 'article','book','book-chapter','dataset','letter','reference-entry','report','review'. This gives us 15089 out of 16480 entries")

paper.details.ws = paper.details.ws %>% filter((grepl('Article',`document type`) | `document type` %in% c('Book','Book chapter', 'Conference paper','Data paper','Editorial Material; Book Chapter','Proceedings Paper', 'Review', 'Short survey')) & !grepl('Retract', `document type`))


tot.papers = nrow(paper.details)

#report the data that we have
printo('We have ',tot.papers,' publications pulled from OpenAlex in our analysis. Of which ', sum(!is.na(paper.details$doi)), 'have DOI information.')
printo()
printo('There are ',nrow(paper.details.ws),' publications pulled from Web of Science and Scopus in our analysis.')
# printo('The data sources of these publications are split as - \n',round(sum(paper.details$datasource == 'Both')/tot.papers*100),"% available in both databases,\n",round(sum(paper.details$datasource == 'Scopus')/tot.papers*100),"% available only from Scopus,\n",round(sum(paper.details$datasource == 'WoS')/tot.papers*100),"% available only from Web of Science.\n")



```


```{r Membership of different databases, echo = F}


match.dois = paper.details %>% filter(!is.na(doi)) %>% select(publication_year,doi,datasource) %>% ungroup() %>%   
  mutate(doi = tolower(str_remove(doi,"https://doi.org/"))) %>%
  full_join(paper.details.ws %>% ungroup() %>% select(year, doi, datasource), by = 'doi') %>%
  replace_na(list(datasource.x ='no', datasource.y = 'no')) %>%
  mutate(Scopus = (datasource.y %in% c('Both','Scopus')),
         WoS = (datasource.y %in% c('Both','WoS')),
         OpenAlex = (datasource.x %in% c('OpenAlex'))) %>%
  select(-datasource.x,-datasource.y) %>% mutate(nSources = Scopus + WoS + OpenAlex)

#Check if there is conflict in publication year for overlapping entries
diff = with(match.dois,publication_year-year)
unmatched_year = match.dois %>% filter(!is.na(diff) & diff != 0) %>%
  mutate(diff = publication_year-year) %>% arrange(desc(abs(diff)))
#After manually checking about 20 entries, it looks like the OpenAlex data is better than our earlier data for publication year, so moving to using that
match.dois = match.dois %>% mutate(publication_year = ifelse(is.na(publication_year), year,publication_year)) %>% select(-year)

df_counts <- as.data.frame(with(match.dois, table(publication_year, Scopus, WoS, OpenAlex)))
colnames(df_counts) <- c("Year","Scopus","WoS","OpenAlex","Count")

# convert logicals and label each combination
df_summary <- df_counts %>%
  mutate(
    Scopus    = as.logical(Scopus),
    WoS       = as.logical(WoS),
    OpenAlex  = as.logical(OpenAlex),
    Source    = case_when(
      Scopus & !WoS   & !OpenAlex ~ "Scopus only",
      !Scopus & WoS   & !OpenAlex ~ "WoS only",
      !Scopus & !WoS  & OpenAlex  ~ "OpenAlex only",
      Scopus & WoS    & !OpenAlex ~ "Scopus & WoS",
      Scopus & !WoS   & OpenAlex  ~ "Scopus & OpenAlex",
      !Scopus & WoS   & OpenAlex  ~ "WoS & OpenAlex",
      Scopus & WoS    & OpenAlex  ~ "All three",
      TRUE                        ~ "None"
    )
  ) %>%
  select(Year,Source, Count) %>%
  arrange(Year,desc(Count))

df_summary = df_summary %>% group_by(Year) %>% summarise(yr_total = sum(Count)) %>%
  right_join(df_summary) %>%
  mutate(pct = round(Count/yr_total*100), Year = as.numeric(Year)) %>% filter(Source != 'None')

ggplot(data = df_summary, aes(x = Year, y = pct, color = Source, shape = Source)) +
  geom_line() + geom_point() + theme_bw()

# install if needed
if (!requireNamespace("ComplexUpset", quietly = TRUE)) {
  install.packages("ComplexUpset")
}
library(ComplexUpset)

# ensure your columns are numeric (0/1)
df_bin <- match.dois %>% 
  transmute(
    Scopus   = as.integer(Scopus),
    WoS      = as.integer(WoS),
    OpenAlex = as.integer(OpenAlex)
  )

upset(
  df_bin,
  intersect     = c("Scopus", "WoS", "OpenAlex"),
  base_annotations = list(
    'Number of records' = intersection_size(counts=TRUE)
  ), #Name = 'Presence in database',
  sort_intersections_by = "degree"
)

## The columns topic.name, subfield.name, field.name and domain.name are a hierarchical classification of the 15,000 papers that are in the paper.details dataframe. So now we will share that hierarchy to visualise


```


```{r Split of research domains, echo = F}

# 1. Domain‐level counts
domain_counts <- paper.details %>%
  count(domain.name) %>%
  arrange(desc(n))

# 2. Domain → Field
domain_field_counts <- paper.details %>%
  count(domain.name, field.name) %>%
  arrange(domain.name, desc(n))

# 3. Domain → Field → Subfield
domain_field_subfield_counts <- paper.details %>%
  count(domain.name, field.name, subfield.name) %>%
  arrange(domain.name, field.name, desc(n))

# 4. Full hierarchy down to Topic
full_breakdown <- paper.details %>%
  count(domain.name, field.name, subfield.name, topic.name) %>%
  arrange(domain.name, field.name, subfield.name, desc(n))

# write_sheet(domain_field_counts, ss = '1WRlXkr4LzLiv6pka8cnPz0tlmid8dbsR9VUo_u-Lh-w',
#             sheet = 'OpenAlex_Domains')
# 
# write_sheet(full_breakdown, ss = '1WRlXkr4LzLiv6pka8cnPz0tlmid8dbsR9VUo_u-Lh-w',
#             sheet = 'OpenAlex_Full')

# Inspect
# print(domain_counts)
# print(domain_field_counts)
# … or View(full_breakdown) in RStudio for the full table

```

```{r}

# install.packages(c("ggplot2", "dplyr"))  # if needed
library(dplyr)
library(ggplot2)

# Filter to your year window and summarise
year_domain <- paper.details %>%
  filter(publication_year >= 2000, publication_year <= 2024) %>%
  count(publication_year, domain.name) %>%
  ungroup()

year_field <- paper.details %>%
  filter(publication_year >= 2000, publication_year <= 2024) %>%
  count(publication_year, field.name) %>%
  ungroup()


# A. Line plot by Domain
ggplot(year_domain, aes(x = publication_year, y = n, color = domain.name)) +
  geom_line(size = 1) +
  scale_x_continuous(breaks = seq(2000, 2024, by = 2)) +
  labs(
    title = "Publications Over Time by Domain",
    x     = "Year",
    y     = "Number of Publications",
    color = "Domain"
  ) +
  theme_minimal()
ggsave('domains over years.jpg')


# B. Line plot by Field
# ggplot(year_field, aes(x = publication_year, y = n, color = field.name)) +
#   geom_line(size = 1) +
#   scale_x_continuous(breaks = seq(2000, 2024, by = 2)) +
#   labs(
#     title = "Publications Over Time by Field",
#     x     = "Year",
#     y     = "Number of Publications",
#     color = "Field"
#   ) +
#   theme_minimal()

# Load required libraries
# install.packages(c("dplyr", "ggplot2"))  # uncomment if needed

# 1. Summarise number of publications per year, per domain and field
year_df <- paper.details %>%
  filter(publication_year >= 2000, publication_year <= 2024) %>%
  count(domain.name, field.name, publication_year) %>%
  ungroup()

# 2. Create an output directory for the plots (optional)
if (!dir.exists("plots")) {
  dir.create("plots")
}

# 3. Loop over each domain, make a line‐plot of fields vs. year, and save as PNG
domains <- unique(year_df$domain.name)

for (dom in domains) {
  # Subset data for this domain
  df_dom <- filter(year_df, domain.name == dom)
  
  # Build the plot
  p <- ggplot(df_dom, aes(x = publication_year, y = n, color = field.name)) +
    geom_line(size = 1) +
    scale_x_continuous(breaks = seq(2000, 2024, by = 2)) +
    labs(
      title = paste("Publications by Field in", dom),
      x     = "Year",
      y     = "Number of Publications",
      color = "Field"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom")
  
  # Sanitize domain name for filename (replace non-alphanumeric with underscores)
  safe_name <- gsub("[^A-Za-z0-9]", "_", dom)
  filename  <- file.path("plots", paste0(safe_name, ".jpg"))
  
  # Save plot to PNG
  ggsave(
    filename = filename,
    plot     = p,
    width    = 8,    # inches
    height   = 6,    # inches
    dpi      = 300
  )
  
  message("Saved plot for domain '", dom, "' to ", filename)
}



```

